---
title: "Carryover_CornResults"
author: "Kolby Grint"
date: "3/4/2021"
output: pdf_document
---


```{r,include = FALSE, echo = FALSE}

library(car)
library(ggplot2)
library(emmeans)
library(lme4)
library(lmerTest)
library(patchwork)
library(glmmTMB)
library(dplyr)
library(tidyverse)
library(multcomp)
```


```{r, include = FALSE}
getwd()

Corn= read.csv(file="Corn_MasterData.csv")

CC= read.csv(file= "CoverCropData.csv")

cnyield= data.frame()

order= c("Tillage", "No-Till", "Cover Crop")
order1= c("CTRL", "FO25", "FO50", "IM25", "IM50")

CornComp= read.csv(file="CornYieldComponents.csv")
Corn$Rep= factor(Corn$Rep)
Corn$Year= factor(Corn$Year)


```


```{r,include = FALSE}
Corn1 <- Corn %>% 
  mutate(Rep = as_factor(Rep),
         Year = as_factor(Year),
         Soil= fct_recode(Soil, 
                          "Cover Crop" = "CC",
                          "No-Till" = "NT",
                          "Tillage" = "Till"),
         Site_crop_yr = fct_recode(Site_crop_yr,
                          "Arlington 2019" = "ARL_CN_19",
                          "Arlington 2020" = "ARL_CN_20",
                          "Lincoln 2019" = "HAV_CN_19",
                          "Lincoln 2020" = "HAV_CN_20",
                          "Lancaster 2019" = "LAN_CN_19",
                          "Lancaster 2020" = "LAN_CN_20"),
         Location = fct_recode(Location,
                               "Arlington" = "Arlington",
                               "Lancaster" = "Lancaster",
                               "Lincoln" = "Havelock"),
         Crop.Canopy = round(Crop.Canopy/100, 2),
         yield = round(yield, 5),
         Stand.Count = round(Stand.Count, 6)) %>%
  filter(!is.na(yield)) %>%
  filter(!is.na(Crop.Canopy)) %>%
  filter(!is.na(Stand.Count)) %>%
  filter(!Site_crop_yr == "Arlington 2020") %>%
  janitor::clean_names()

CornCC <- CC %>%
  filter(Crop == "Corn") %>%
  mutate(Rep = as_factor(Rep),
         Year = as_factor(Year),
         Site_Crop_Yr = fct_recode(Site_crop_yr,
                          "Arlington 2019" = "ARL_CN_19",
                          "Arlington 2020"  = "ARL_CN_20",
                          "Lincoln 2019" = "HAV_CN_19",
                          "Lincoln 2020" = "HAV_CN_20",
                          "Lancaster 2019" = "LAN_CN_19",
                          "Lancaster 2020" = "LAN_CN_20"),
         Site = fct_recode(Site,
                               "Arlington" = "Arlington",
                               "Lancaster" = "Lancaster",
                               "Lincoln" = "Havelock"),
         Canopy = round(Canopy/100, 3)) %>%
  filter(!is.na(Biomass_kg)) %>%
  filter(!is.na(Site_crop_yr)) %>% 
  filter(!Site_crop_yr == "Arlington 2020") %>%
  janitor::clean_names()


CornComp= CornComp %>% 
  mutate(Location = fct_recode(Location,
                               "Arlington" = "ARL",
                               "Lancaster" = "LAN",
                               "Lincoln" = "HAV"),
         Soil = fct_recode(Soil,
                           "Cover Crop" = "CC",
                          "No-Till" = "NT",
                          "Tillage" = "Till")) %>%
  filter(Site_Yr != "ARL_20") %>%
  filter(!is.na(Total)) %>%
  filter(!is.na(Hundred)) %>%
  filter(!is.na(Seeds)) %>%
  janitor::clean_names()

```
# Analysis Procedure

Prior to analysis I took the approach of plotting the response variables with box-plots to visualize treatment differences with soil management between locations. The intention of this was to visualize the differences between locations as well determine if I feel comfortable pooling things within a location (not testing for a site-year or year effect). This has been the desired direction to simplify results for publication. When I didn't feel the data allowed for this I tested for differences between site-years in a condensed model. This approach is up for more discussion, as it eliminates the potential to view anomalies in the data which might be insightful and scientifically interesting. We are assuming editors won't like complex findings.


I would also like to point out that for every linear-mixed-effects model I am testing to see that the model meets the visual assumptions for normal distribution of residual and evenly distributed variance. I will demonstrate for the first model, and only include it in the output for future analyses when it is suspected that transformations need to be made.

More analyses were made than are going to be included in this pdf. I chose not to include them all so as to condense the output to the approach and considerations that I think are most valuable for the publication.

## Removing the Arlington 2020 Site-year
After some consideration and evaluating some analyses we decided to remove the Arlington 2020 site-year for corn from all analyses. There was an establishment issue with this site-year (Kolby used the wrong map to lay out herbicide treatments) and a suspected fertility misapplication that reduced yield for part of the trial.

# Early Season Stand Counts

```{r, fig.width= 12, fig.height= 6}
Corn1 %>%
  ggplot(aes(x = soil, y = stand_count, color = location)) +
  geom_boxplot() +
  facet_grid(crop ~ year)
```

```{r, fig.width= 12, fig.height= 6}
Corn1 %>%
  ggplot(aes(x = herb, y = stand_count, color = location)) +
  geom_boxplot() +
  facet_grid(soil ~ year)

```

Based on these visual representations it doesn't appear to me that there are really any consistent patterns as a function of soil management, herbicide treatment, location, or year. There does appear to be differences in location across seasons. Therefore, I think it is best if we test for site-year differences as a fixed effect in models for our initial approach and separate means by site-year where appropriate.

```{r, include= FALSE}
Corn1 <- Corn1 %>%
  filter(!site_crop_yr == "Arlington 2020")
```

## Condensed Stand Count Model
```{r}
cn_stand= lmer(stand_count ~ site_crop_yr*soil*herb + (1|site_crop_yr:rep), data= Corn1)

qqnorm(resid(cn_stand))

plot(cn_stand)
#assumptions met satisfactorily

anova(cn_stand)
#site-year significant
```
Herbicide carryover and soil management had no effect on early season stand counts in corn.

```{r, include= FALSE}
cn_stand_lsmeans= lsmeans(cn_stand,~ site_crop_yr, contr="pairwise", adjust="none", type="response")
cn_standCLD<- CLD(cn_stand_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

cn_standCLD <- as_tibble(cn_standCLD) %>% 
  rename(stand_count = lsmean) %>%
  mutate(site_crop_yr = fct_recode(site_crop_yr,
                          "Arlington 2019" = "ARL_CN_19",
                          "Havelock 2019" = "HAV_CN_19",
                          "Havelock 2020" = "HAV_CN_20",
                          "Lancaster 2019" = "LAN_CN_19",
                          "Lancaster 2020" = "LAN_CN_20")) %>%
  arrange(site_crop_yr)
```



```{r, echo= FALSE}
ggplot(cn_standCLD, aes(x= site_crop_yr, y= stand_count, color= site_crop_yr)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3) +
  geom_text(aes(label = .group), nudge_y = 3500, size= 5) +
  geom_jitter(data = Corn1 ,mapping = aes(y = stand_count), alpha = 0.2) +
  #coord_flip() +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Corn Stand Counts")
```
Wisconsin Stand counts should be closer to 80,000 and Havelock should be closer to 79,000


# Corn Canopy

```{r}
Corn1 %>%
  ggplot(aes(x = soil, y = crop_canopy, color = location)) +
  geom_boxplot() +
  facet_grid(crop ~ year)
```
Based on the variability in canopy coverage between cropping seasons within a location, 
I created a condensed model, similar to the stand count model, with site-year as 
a fixed effect.

I also decided to perform the analysis using a separate model for each site-year. 
The first model and figures resulting from this analysis will also be displayed.

## Condensed analysis
```{r}
cn_canopy = glmmTMB(crop_canopy~ soil*herb*site_crop_yr + (1|rep:site_crop_yr), data= Corn1, beta_family(link="logit"))
#no assumptions to meet.

Anova(cn_canopy)
#all 3 main fixed effects significant and the soil:site-year interaction
```

```{r, include= FALSE}
cn_canopy_herbemmeans = emmeans(cn_canopy, ~ herb, contr= "pairwise", adjust= "none", type= "response")
cn_canopy_herbCLD = CLD(cn_canopy_herbemmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

cn_canopy_herbCLD <- as_tibble(cn_canopy_herbCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(herb= factor(herb, levels= order1)) %>%
  arrange(herb)

cn_canopy_soilemmeans = emmeans(cn_canopy, ~ soil|site_crop_yr, contr= "pairwise", adjust= "none", type= "response")
cn_canopy_soilCLD = CLD(cn_canopy_soilemmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

cn_canopy_soilCLD <- as_tibble(cn_canopy_soilCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```


```{r}
cn_canopy_soilCLD = cn_canopy_soilCLD %>%
  separate(site_crop_yr, c("location", "year"), " ") %>%
  mutate(year = as.factor(year))

```


```{r, include= FALSE}
cn_canopyherb <- ggplot(cn_canopy_herbCLD, aes(x= herb, y= crop_canopy*100, color= herb)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL*100, ymax= upper.CL*100), width= .3) +
  geom_text(aes(label = .group), nudge_y = 12, size= 6) +
  geom_jitter(data = Corn1 ,mapping = aes(y = crop_canopy*100), alpha = 0.2) +
  #coord_flip() +
  #facet_wrap(~site_crop_yr) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none",
        plot.title = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        axis.text.y = element_text(size = 15),
        axis.text.x = element_text(size = 15)) +
  labs(x= "Herbicide Treatment", y= "% Canopy Coverage")
```


```{r, include= FALSE}
cn_canopy <- ggplot(cn_canopy_soilCLD, aes(x= soil, y= crop_canopy*100, color= soil)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL*100, ymax= upper.CL*100), width= .3) +
  geom_text(aes(label = .group), nudge_y = 12, size= 6) +
  geom_jitter(data = Corn1 ,mapping = aes(y = crop_canopy*100), alpha = 0.2) +
  #coord_flip() +
  facet_grid(year~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none",
        plot.title = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        axis.text.y = element_text(size = 15),
        axis.text.x = element_text(angle= 45, hjust = 1, size = 15),
        strip.text = element_text(size= 15)) +
  labs(x= "Soil Management Practice", y= "% Canopy Coverage")
```



## Separated analysis for each site-year
Just showing the first one and then hiding later ones.
```{r,}
#begining of analysis with new model for each site-year
arl19_corn_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Corn1, site_crop_yr == "Arlington 2019")), beta_family(link="logit"))

Anova(arl19_corn_can)
#Soil was significant
```

```{r, include= FALSE}
arl19_corn_can_lsmeans= emmeans(arl19_corn_can ,~ soil, contr="pairwise", adjust="none", type="response")
arl19_corn_canCLD<- CLD(arl19_corn_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

arl19_corn_canCLD <- as_tibble(arl19_corn_canCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```


```{r, include= FALSE}
lan19_corn_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Corn1, site_crop_yr == "Lancaster 2019")), beta_family(link="logit"))

Anova(lan19_corn_can)
#Soil was significant

lan20_corn_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Corn1, site_crop_yr == "Lancaster 2020")), beta_family(link="logit"))

Anova(lan20_corn_can)
#Soil was significant
```


```{r, include= FALSE}
lan19_corn_can_lsmeans= emmeans(lan19_corn_can ,~ soil, contr="pairwise", adjust="none", type="response")
lan19_corn_canCLD<- CLD(lan19_corn_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan19_corn_canCLD <- as_tibble(lan19_corn_canCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)

lan20_corn_can_lsmeans= emmeans(lan20_corn_can ,~ soil, contr="pairwise", adjust="none", type="response")
lan20_corn_canCLD<- CLD(lan20_corn_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan20_corn_canCLD <- as_tibble(lan20_corn_canCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```


```{r, include= FALSE}
hav19_corn_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Corn1, site_crop_yr == "Havelock 2019")), beta_family(link="logit"))

Anova(hav19_corn_can)
#soil management fixed effect was significant

hav20_corn_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Corn1, site_crop_yr == "Havelock 2020")), beta_family(link="logit"))

Anova(hav20_corn_can)
#nothing was significant
```

```{r, include= FALSE}
hav19_corn_can_lsmeans= emmeans(hav19_corn_can ,~ soil, contr="pairwise", adjust="none", type="response")
hav19_corn_canCLD<- CLD(hav19_corn_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav19_corn_canCLD <- as_tibble(hav19_corn_canCLD) %>%
 rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)

hav20_corn_can_lsmeans= emmeans(hav20_corn_can ,~ soil, contr="pairwise", adjust="none", type="response")
hav20_corn_canCLD<- CLD(hav20_corn_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav20_corn_canCLD <- as_tibble(hav20_corn_canCLD) %>%
 rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, include= FALSE}
cncanopy= data.frame()

arl19_corn_canCLD$location= c("Arlington")
lan19_corn_canCLD$location= c("Lancaster")
lan20_corn_canCLD$location= c("Lancaster")
hav19_corn_canCLD$location= c("Havelock")
hav20_corn_canCLD$location= c("Havelock")

arl19_corn_canCLD$year= c("2019")
lan19_corn_canCLD$year= c("2019")
lan20_corn_canCLD$year= c("2020")
hav19_corn_canCLD$year= c("2019")
hav20_corn_canCLD$year= c("2020")

cncanopy<- rbind(arl19_corn_canCLD, cncanopy)
cncanopy<- rbind(lan19_corn_canCLD, cncanopy)
cncanopy<- rbind(lan20_corn_canCLD, cncanopy)
cncanopy<- rbind(hav19_corn_canCLD, cncanopy)
cncanopy<- rbind(hav20_corn_canCLD, cncanopy)
```


```{r, include= FALSE}
cn_canopy1 <- ggplot(cncanopy, aes(x= soil, y= crop_canopy*100, color= soil)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL*100, ymax= upper.CL*100), width= .3) +
  geom_text(aes(label = .group), nudge_y = 12) +
  geom_jitter(data = Corn1 ,mapping = aes(y = crop_canopy*100), alpha = 0.2) +
  #coord_flip() +
  facet_grid(year~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Corn Canopy")
```

## Comparison of canopy coverage analysis approaches

### Separated

```{r, echo= FALSE}
cn_canopy1
```

### Condensed

```{r, include= FALSE}
composite1<- {cn_canopyherb + cn_canopy }+
  plot_annotation(title = 'Corn Canopy Coverage',
                  subtitle = 'V3-V4 Crop Stage',
  theme = theme(plot.title = element_text(size = 30),
                plot.subtitle= element_text(size = 20))) 
```

```{r, echo= FALSE, fig.height= 6, fig.width= 12}
composite1
```

There were slight differences in the Lancaster 2019 site-year results between analysis approaches. The separated approach didn't show that herbicide treatment had a significant effect on canopy coverage but in the composite approach there was reduced coverage for the imazethapyr half-rate treatment, although not significantly different from the control treatment. I prefer the results from the composite approach, similar to my selection in soybean.


# Corn Yield

```{r}
Corn1 %>%
  ggplot(aes(x = herb, y = yield, color = herb)) +
  geom_boxplot() +
  facet_grid(location ~ year)
```

```{r}
Corn1 %>%
  ggplot(aes(x = soil, y = yield, color = location)) +
  geom_boxplot() +
  facet_grid(crop ~ year)
```
Doesn't appear as if herbicides are likely having any effect on corn yield. It does appear that there are similar trends and yield within a location across years. I will proceed with performing a separate analysis for each location.

### Arlington 2019 Analysis
Only going to show the first model. Repeated for each location.
```{r, fig.show= 'hide'}
arlcn_yield1= lmer(yield~ soil*herb + (1|rep:site_crop_yr), data= (filter(Corn1, site_crop_yr == "Arlington 2019")))

qqnorm(resid(arlcn_yield1))

plot(arlcn_yield1)
#assumptions look good
```

```{r}
anova(arlcn_yield1)
#soil managment fixed effect significant
```

### Lancaster Analysis
```{r, include= FALSE}
lancn_yield= lmer(yield~ soil*herb + (1|rep/year), data= (filter(Corn1, location == "Lancaster")))

qqnorm(resid(lancn_yield))

plot(lancn_yield)
#assumptions look good
```

```{r}
anova(lancn_yield)
#Soil management fixed effect significant
```


### Havelock Analysis
```{r, include= FALSE}
havcn_yield= lmer(yield~ soil*herb + (1|rep/year), data= (filter(Corn1, location == "Lincoln")))
#from my understanding the "boundary (singular) fit: see ?isSingular" error means that the estimate of error between random effects, in this case rep/year is almost zero, meaning there isn't a lot of random variability?

qqnorm(resid(havcn_yield))

plot(havcn_yield)
#assumptions look good
```

```{r}
anova(havcn_yield)
#soil management significant
```


```{r, include= FALSE}
arl_cn_lsmeans<- lsmeans(arlcn_yield1, ~ soil, contr="pairwise", adjust="none")

arl_cn_cld <- cld(arl_cn_lsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

arl_cn_cld <- as_tibble(arl_cn_cld) %>% 
  rename(yield = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, include= FALSE}
lan_cn_lsmeans<- lsmeans(lancn_yield, ~ soil, contr="pairwise", adjust="none")

lan_cn_cld <- cld(lan_cn_lsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan_cn_cld <- as_tibble(lan_cn_cld) %>% 
  rename(yield = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, include= FALSE}
hav_cn_lsmeans<- lsmeans(havcn_yield, ~ soil, contr="pairwise", adjust="none")

hav_cn_cld <- cld(hav_cn_lsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav_cn_cld <- as_tibble(hav_cn_cld) %>% 
  rename(yield = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```


```{r, include= FALSE}
arl_cn_cld$location= c("Arlington")
lan_cn_cld$location= c('Lancaster')
hav_cn_cld$location= c('Lincoln')

cnyield<- rbind(arl_cn_cld, cnyield)
cnyield<- rbind(lan_cn_cld, cnyield)
cnyield<- rbind(hav_cn_cld, cnyield)
```

```{r, include = FALSE}
ylab.text1= expression("Yield kg ha"^"-1")

y1<- ggplot(cnyield, aes(x= soil, y= yield, color= soil)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3) +
  geom_text(aes(label = .group), nudge_y = 2500, size= 6) +
  geom_jitter(data = Corn1 ,mapping = aes(y = yield), alpha = 0.2) +
  #coord_flip() +
  facet_grid(~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none",
        plot.title = element_text(size = 25),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 25),
        axis.text.x = element_text(size = 15),
        strip.text = element_text(size= 15)) +
  labs(title = "Corn Yield", y= bquote('Yield'~(kg~ha^-1)))
```

```{r, echo= FALSE, fig.width= 10}
y1
```
No impact on crop yield from herbicides. All three location had reduced yield for the CC treatment. Havelock and Lancaster showed reduced yield for the no-till treatment as well.

Now to see if the yield components explain more.

# Corn Yield Components

```{r, include= FALSE}
#CornComp %>% 
  #ggplot(aes(x =Total)) +
  #geom_density()

CornComp %>% 
  ggplot(aes(x =hundred)) +
  geom_density()

CornComp %>% 
  ggplot(aes(x =seeds)) +
  geom_density()
```


```{r}
#CornComp %>%
  #ggplot(aes(x = Soil, y = Total, color = Soil)) +
  #geom_boxplot() +
  #facet_grid(~ Site_Yr)

#Plot of seed density
CornComp %>%
  ggplot(aes(x = soil, y = hundred, color = soil)) +
  geom_boxplot() +
  facet_grid(~ site_yr)

#Plot of seed counts
CornComp %>%
  ggplot(aes(x = soil, y = seeds, color = soil)) +
  geom_boxplot() +
  facet_grid(~ site_yr)
```

Based on these figures I think it would be appropriate to conduct analyses for each location separately similar to how yield was done.

### All yield component Figures will be included at the end of this section.

```{r, include= FALSE}
arl_CNTotal= lmer(total~ soil*herb + (1|rep) , data= (filter(CornComp, location == "Arlington" )))
qqnorm(resid(arl_CNTotal))
plot(arl_CNTotal)
#Assumptions met

anova(arl_CNTotal)
#Nothing significant
```

```{r, include= FALSE}
lan_CNTotal= lmer(total~ soil*herb + (1|rep) , data= (filter(CornComp, location == "Lancaster" )))
qqnorm(resid(lan_CNTotal))
plot(lan_CNTotal)
#Assumptions met

anova(lan_CNTotal)
#Soil significant
```

```{r, include= FALSE}
hav_CNTotal= lmer(total~ soil*herb + (1|rep) , data= (filter(CornComp, location == "Havelock" )))
qqnorm(resid(hav_CNTotal))
plot(hav_CNTotal)
#Assumptions met

anova(hav_CNTotal)
#Nothing significant
```

```{r, echo= FALSE, include= FALSE}
arl_cn_Totallsmeans<- lsmeans(arl_CNTotal, ~ soil, contr="pairwise", adjust="none")

arl_cn_Totalcld <- cld(arl_cn_Totallsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

arl_cn_Totalcld <- as_tibble(arl_cn_Totalcld) %>% 
  rename(total = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, echo= FALSE, include= FALSE}
lan_cn_Totallsmeans<- lsmeans(lan_CNTotal, ~ soil, contr="pairwise", adjust="none")

lan_cn_Totalcld <- cld(lan_cn_Totallsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan_cn_Totalcld <- as_tibble(lan_cn_Totalcld) %>% 
  rename(total = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, echo= FALSE, include= FALSE}
hav_cn_Totallsmeans<- lsmeans(hav_CNTotal, ~ soil, contr="pairwise", adjust="none")

hav_cn_Totalcld <- cld(hav_cn_Totallsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav_cn_Totalcld <- as_tibble(hav_cn_Totalcld) %>% 
  rename(total = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```


```{r, echo= FALSE, include= FALSE}
cn_Total= data.frame()

arl_cn_Totalcld$location= c("Arlington")
lan_cn_Totalcld$location= c("Lancaster")
hav_cn_Totalcld$location= c("Havelock")

cn_Total<- rbind(arl_cn_Totalcld, cn_Total)
cn_Total<- rbind(lan_cn_Totalcld, cn_Total)
cn_Total<- rbind(hav_cn_Totalcld, cn_Total)

```


```{r, echo= FALSE, include= FALSE}
CNTotal_site<- ggplot(cn_Total, aes(x= soil, y= total, color= soil)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3) +
  geom_text(aes(label = .group), nudge_y = 210) +
  geom_jitter(data = CornComp ,mapping = aes(y = total), alpha = 0.2) +
  #coord_flip() +
  facet_grid(~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Corn Total Sample")
```




```{r, include = FALSE, echo = FALSE}
#Condensed analysis for total sample mass.
CNTotal= lmer(total~site_yr*soil*herb+ (1|site_yr:rep) , data=CornComp)
qqnorm(resid(CNTotal))
plot(CNTotal)
#normality is questionable, data looks a little skewed. Try transforming.

CNTotal1= lmer((total^2)~site_yr*soil*herb+ (1|site_yr:rep) , data=CornComp)
qqnorm(resid(CNTotal1))
plot(CNTotal1)
#slightly improved on normality maybe. I think I will leave it untransformed since transformation isn't fitting of data type.
```


```{r, include = FALSE, echo = FALSE}
anova(CNTotal)
#2-way interaction between SIte-year and soil. Site-year and soil management main effects also significant.
```

```{r, echo= FALSE, include= FALSE}
CNTotMeans= lsmeans(CNTotal, ~ soil|site_yr, contr="pairwise", adjust="none", type= "response")
CLD1= CLD(CNTotMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD1
```


```{r, echo= FALSE, include= FALSE}
CNTotal= ggplot(CLD1, aes(x=soil , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 150, size = 8)+
  facet_grid(~site_yr)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Corn Total Sample Mass", x= "Soil Management", y= "Total Sample Mass")

```

```{r, echo= FALSE, include= FALSE}
CNTotal
```

## Corn Seed Density

### Arlington
Only chose to show the first model
```{r, fig.show='hide'}
arl_CNHun= lmer(hundred~ soil*herb + (1|rep) , data= (filter(CornComp, location == "Arlington" )))
qqnorm(resid(arl_CNHun))
plot(arl_CNHun)
#Assumptions met
```

```{r}
anova(arl_CNHun)
#Soil Significant
```

### Lancaster
```{r, include= FALSE}
lan_CNHun= lmer(hundred~ soil*herb + (1|rep/year) , data= (filter(CornComp, location == "Lancaster" )))
qqnorm(resid(lan_CNHun))
plot(lan_CNHun)
#Assumptions met
```

```{r}
anova(lan_CNHun)
#Soil significant
```

### Havelock
```{r, include= FALSE}
hav_CNHun= lmer(hundred~ soil*herb + (1|rep/year) , data= (filter(CornComp, location == "Lincoln" )))
qqnorm(resid(hav_CNHun))
plot(hav_CNHun)
#Assumptions met
```

```{r}
anova(hav_CNHun)
#Soil significant
```

```{r, echo= FALSE, include= FALSE}
arl_CNHunlsmeans<- lsmeans(arl_CNHun, ~ soil, contr="pairwise", adjust="none")

arl_CNHuncld <- cld(arl_CNHunlsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

arl_CNHuncld <- as_tibble(arl_CNHuncld) %>% 
  rename(hundred = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, echo= FALSE, include= FALSE}
lan_CNHunlsmeans<- lsmeans(lan_CNHun, ~ soil, contr="pairwise", adjust="none")

lan_CNHuncld <- cld(lan_CNHunlsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan_CNHuncld <- as_tibble(lan_CNHuncld) %>% 
  rename(hundred = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, echo= FALSE, include= FALSE}
hav_CNHunlsmeans<- lsmeans(hav_CNHun, ~ soil, contr="pairwise", adjust="none")

hav_CNHuncld <- cld(hav_CNHunlsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav_CNHuncld <- as_tibble(hav_CNHuncld) %>% 
  rename(hundred = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```


```{r, echo= FALSE, include= FALSE}
cn_Hundred= data.frame()

arl_CNHuncld$location= c("Arlington")
lan_CNHuncld$location= c("Lancaster")
hav_CNHuncld$location= c("Lincoln")


cn_Hundred<- rbind(arl_CNHuncld, cn_Hundred)
cn_Hundred<- rbind(hav_CNHuncld, cn_Hundred)
cn_Hundred<- rbind(lan_CNHuncld, cn_Hundred)

cn_Hundred<- cn_Hundred %>%
  arrange(location)

```


```{r, echo= FALSE, include= FALSE}

CNHundred_site<- ggplot(cn_Hundred, aes(x= soil, y= hundred, color= soil)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3) +
  geom_text(aes(label = .group), nudge_y = 6, size= 6) +
  geom_jitter(data = CornComp ,mapping = aes(y = hundred), alpha = 0.2) +
  #coord_flip() +
  facet_grid(~ location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none",
        plot.title = element_text(size = 25),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 25),
        axis.text.x = element_text(size = 15),
        strip.text = element_text(size= 15)) +
  labs(title = "Corn Seed Density",  y= bquote('100 Seed Mass'~(g)))
```




```{r, include = FALSE, echo = FALSE }
## Condensed Analysis----- not included in pdf
CNHundred= lmer(hundred~site_yr*soil*herb+ (1|site_yr:rep) , data=CornComp)
qqnorm(resid(CNHundred))
plot(CNHundred)
#Assumptions for normality and equal variance satisfactorily met. Proceed with ANOVA.
```


```{r, include = FALSE, echo = FALSE }
anova(CNHundred)
#2-way interaction between SIte-year and soil. Site-year and soil management main effects also significant.
```


```{r, include = FALSE, echo = FALSE }
CNHundredMeans= lsmeans(CNHundred, ~ soil|site_yr, contr="pairwise", adjust="none", type= "response")
CLD2= CLD(CNHundredMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD2
```


```{r, echo= FALSE, include= FALSE}
CNSeedDensity= ggplot(CLD2, aes(x=soil , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 2, size = 8)+
  facet_grid(~site_yr)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Corn Seed Density",  y= "100 Seed Weight")

```

```{r, echo= FALSE, include= FALSE}
CNSeedDensity
```

## Corn Seed Count

## Analysis by Location

### Arlington
Showing first model only
```{r, echo= FALSE}
arl_Seeds= lmer(seeds~ soil*herb + (1|rep) , data= (filter(CornComp, location == "Arlington" )))
qqnorm(resid(arl_Seeds))
plot(arl_Seeds)
#Assumptions met
```

```{r}
anova(arl_Seeds)
#Nothing Significant
```
### Lancaster
```{r, include=FALSE}
lan_Seeds= lmer(seeds~ soil*herb + (1|rep/year) , data= (filter(CornComp, location == "Lancaster" )))
qqnorm(resid(lan_Seeds))
plot(lan_Seeds)
#Normality slightly questionable, Equal variance good
```

```{r}
anova(lan_Seeds)
#Soil significant
```

### Havelock
```{r, include= FALSE}
hav_Seeds= lmer(seeds~ soil*herb + (1|rep/year) , data= (filter(CornComp, location == "Lincoln" )))
qqnorm(resid(hav_Seeds))
plot(hav_Seeds)
#Assumptions met
```

```{r}
anova(hav_Seeds)
#Nothing significant
```

```{r, echo= FALSE, include= FALSE}
arl_Seedslsmeans<- lsmeans(arl_Seeds, ~ soil, contr="pairwise", adjust="none")

arl_Seedscld <- cld(arl_Seedslsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

arl_Seedscld <- as_tibble(arl_Seedscld) %>% 
  rename(seeds = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, echo= FALSE, include= FALSE}
lan_Seedslsmeans<- lsmeans(lan_Seeds, ~ soil, contr="pairwise", adjust="none")

lan_Seedscld <- cld(lan_Seedslsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan_Seedscld <- as_tibble(lan_Seedscld) %>% 
  rename(seeds = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, echo= FALSE, include= FALSE}
hav_Seedslsmeans<- lsmeans(hav_Seeds, ~ soil, contr="pairwise", adjust="none")

hav_Seedscld <- cld(hav_Seedslsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav_Seedscld <- as_tibble(hav_Seedscld) %>% 
  rename(seeds = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```


```{r, echo= FALSE, include= FALSE}
cn_Seeds= data.frame()

arl_Seedscld$location= c("Arlington")
lan_Seedscld$location= c("Lancaster")
hav_Seedscld$location= c("Lincoln")

cn_Seeds<- rbind(arl_Seedscld, cn_Seeds)
cn_Seeds<- rbind(lan_Seedscld, cn_Seeds)
cn_Seeds<- rbind(hav_Seedscld, cn_Seeds)


```


```{r, echo= FALSE, include= FALSE}
ylab.text2= expression("Seeds Sample"^"-1")

CNSeeds_site<- ggplot(cn_Seeds, aes(x= soil, y= seeds, color= soil)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3) +
  geom_text(aes(label = .group), nudge_y = 900, size= 6) +
  geom_jitter(data = CornComp ,mapping = aes(y = seeds), alpha = 0.2) +
  #coord_flip() +
  facet_grid(~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none",
        plot.title = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        axis.text.x = element_text(size = 15),
        strip.text = element_text(size= 15)) +
  labs(title = "Corn Seed Count", x= "Soil Management Practice", y= bquote('Seed Count'~(seeds)))
```


```{r, include = FALSE, echo = FALSE }
#Condensed Analysis------- Not included in pdf
CNSeeds= lmer(seeds~site_yr*soil*herb+ (1|site_yr:rep) , data=CornComp)
qqnorm(resid(CNSeeds))
plot(CNSeeds)
#Normality assumption isn't amazing Proceed to transform

CNSeeds1= lmer((seeds^2)~site_yr*soil*herb+ (1|site_yr:rep) , data=CornComp)
qqnorm(resid(CNSeeds1))
plot(CNSeeds1)
#Assumption for normal distribution improved. This transformation doesn't really make sense for this data, so proceeded with first model.
```


```{r, include = FALSE, echo = FALSE}
anova(CNSeeds)
#2-way interaction between SIte-year and soil. Site-year and soil management main effects also significant.
```

```{r, include = FALSE, echo = FALSE}
CNSeedsMeans= lsmeans(CNSeeds, ~ soil|site_yr, contr="pairwise", adjust="none", type= "response")
CLD3= CLD(CNSeedsMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD3
```


```{r, echo= FALSE, include= FALSE}
CNSeeds= ggplot(CLD3, aes(x=soil , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 400, size = 8)+
  facet_grid(~site_yr)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Corn Seed Count", x= "Soil Management", y= "# of Seeds")
```

```{r, echo= FALSE, include= FALSE}
CNSeeds
```

```{r, include = FALSE, echo = FALSE}
CNTotal
CNSeedDensity
CNSeeds
#End of condensed
```


# Corn Yield Components to Yield comparison
```{r, include= FALSE}

Yield_figure= {(y1)/(CNHundred_site)/(CNSeeds_site)}+
  plot_annotation(tag_levels = ('A')) &
  theme(plot.title = element_text(size = 40),
                plot.tag= element_text(size= 40))
```

```{r, echo= FALSE, fig.height= 13, fig.width= 12}
Yield_figure
```
 

# Cover Crop Biomass analysis
```{r}
CornCC %>%
  ggplot(aes(x = herb, y = biomass_kg, color = site)) +
  geom_boxplot() +
  facet_grid(crop ~ year)
```
based on separations between locations and across years, I think it is appropriate to look for significant differences between site-years and separate means accordingly in CC biomass models.

```{r}
cn_cc_bio= lmer(biomass_kg~ site_crop_yr * herb + (1|site_crop_yr:rep), data=CornCC)

qqnorm(resid(cn_cc_bio))
plot(cn_cc_bio)
#Assumption for equal variance not met

#Proceeded with a square-root transformation
cn_cc_bio1= lmer(sqrt(biomass_kg)~ site_crop_yr * herb + (1|site_crop_yr:rep), data=CornCC)

qqnorm(resid(cn_cc_bio1))
plot(cn_cc_bio1)
#assumptions improved. Use this one!

anova(cn_cc_bio1)
#Site-year significant
```
There is no evidence that herbicide treatment influenced cover crop biomass.

```{r, echo= FALSE, include= FALSE}
cn_cc_lsmeans= emmeans(cn_cc_bio1 ,~ site_crop_yr, contr="pairwise", adjust="none", type="response")
cn_ccCLD<- CLD(cn_cc_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

cn_ccCLD <- as_tibble(cn_ccCLD) %>%
 rename(biomass_kg = response)
```


```{r, echo= FALSE, include= FALSE}
Corn_CCbio= ggplot(cn_ccCLD, aes(x= site_crop_yr, y= biomass_kg, color= site_crop_yr)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3) +
  geom_text(aes(label = .group), nudge_y = 150, size= 5) +
  geom_jitter(data = CornCC ,mapping = aes(y = biomass_kg), alpha = 0.2) +
  coord_flip() +
  #facet_grid(year~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Corn")
```

```{r, include= FALSE}
Corn_CCbio
```


# Cover Crop Canopy

```{r, echo= FALSE, include= FALSE}
CornCC1 <- CornCC %>%
  filter(!is.na(canopy))

```

```{r}
CornCC1 %>%
  ggplot(aes(x = herb, y = canopy, color = site)) +
  geom_boxplot() +
  facet_grid(crop ~ year)
```

Based on differences between location across growing seasons I thought it was best to proceed with testing site-year as a fixed effect.

```{r}
cn_cc_can= glmmTMB(canopy~ site_crop_yr*herb + (1|site_crop_yr:rep), data=CornCC1, beta_family(link="logit"))

Anova(cn_cc_can)
#Site-year significant
```

There is no evidence that herbicide treatment influenced cover crop biomass.

```{r, echo= FALSE, include= FALSE}
cn_cc_can_lsmeans= emmeans(cn_cc_can ,~ site_crop_yr, contr="pairwise", adjust="none", type="response")
cn_cc_canCLD<- CLD(cn_cc_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

cn_cc_canCLD <- as_tibble(cn_cc_canCLD) %>%
 rename(canopy = response)
```

```{r, echo= FALSE, include= FALSE}
Corn_CCcan= ggplot(cn_cc_canCLD, aes(x= site_crop_yr, y= canopy*100, color= site_crop_yr)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL*100, ymax= upper.CL*100), width= .3) +
  geom_text(aes(label = .group), nudge_y = 5, size= 5) +
  geom_jitter(data = CornCC1,mapping = aes(y = canopy*100), alpha = 0.2) +
  coord_flip() +
  #facet_grid(year~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Corn")
```

```{r, include= FALSE}
Corn_CCcan
```

