---
title: "Carryover_SoyResults"
author: "Kolby Grint"
date: "3/4/2021"
output: pdf_document
---


```{r, include= FALSE}
library(car)
library(ggplot2)
library(emmeans)
library(lme4)
library(lmerTest)
library(patchwork)
library(glmmTMB)
library(dplyr)
library(tidyverse)
library(multcomp)
```



```{r}
getwd()

Soybean= read.csv(file="Soybean_MasterData.csv")

Soybean= read.csv(file="SBYieldComponents.csv")
Soybean$Rep= factor(Soybean$Rep)
Soybean$Year= factor(Soybean$Year)

CC= read.csv(file= "CoverCropData.csv")

order= c("Tillage", "No-Till", "Cover Crop")
order2= c("CTRL", "CL25", "CL50", "ME25", "ME50")
```


```{r,}

Soybean2= Soybean %>%
  filter(!is.na(Total)) %>%
  filter(!is.na(Hundred)) %>%
  filter(!is.na(Seeds))


Soybean1 <- Soybean %>% 
  mutate(Rep = as_factor(Rep),
         Year = as_factor(Year),
         Soil= fct_recode(Soil, 
                          "Cover Crop" = "NT+CC",
                          "No-Till" = "NT",
                          "Tillage" = "Till"),
         Site_crop_yr = fct_recode(Site_crop_yr,
                          "Arlington 2019" = "ARL_SB_19",
                          "Arlington 2020" = "ARL_SB_20",
                          "Havelock 2019" = "HAV_SB_19",
                          "Havelock 2020" = "HAV_SB_20",
                          "Lancaster 2019" = "LAN_SB_19",
                          "Lancaster 2020" = "LAN_SB_20"),
         Crop.Canopy = round(Crop.Canopy/100, 2),
         yield = round(yield, 4)) %>%
  filter(!is.na(yield)) %>%
  filter(!is.na(Crop.Canopy)) %>%
  filter(!is.na(Stand.Count)) %>%
  janitor::clean_names()

SBCC <- CC %>%
  filter(Crop == "Soybean") %>%
  mutate(Rep = as_factor(Rep),
         Year = as_factor(Year),
         Site_Crop_Yr = fct_recode(Site_Crop_Yr,
                          "Arlington 2019" = "ARL_SB_19",
                          "Arlington 2020"  = "ARL_SB_20",
                          "Havelock 2019" = "HAV_SB_19",
                          "Havelock 2020" = "HAV_SB_20",
                          "Lancaster 2019" = "LAN_SB_19",
                          "Lancaster 2020" = "LAN_SB_20"),
         Canopy = round(Canopy/100, 3)) %>%
  filter(!is.na(Biomass_kg)) %>%
  janitor::clean_names()
```


# Stand Counts
```{r, fig.width= 12, fig.height= 6}
Soybean1 %>%
  ggplot(aes(x = soil, y = stand_count, color = location)) +
  geom_boxplot() +
  facet_grid( ~ year)
```

```{r, fig.width= 12, fig.height= 6}
Soybean1 %>%
  ggplot(aes(x = herb, y = stand_count, color = location)) +
  geom_boxplot() +
  facet_grid(soil~ year)
```


Based on these visual representations it doesn't appear to me that there are really any consistent patterns as a function of soil management, herbicide treatment, location, or year. There does appear to be differences in location across seasons. Therefore, I think it is best if we test for site-year differences as a fixed effect in models for our initial approach and separate means by site-year where appropriate.


### Soybean
```{r}
sb_stand= lmer(stand_count~ site_crop_yr*soil*herb + (1|site_crop_yr:rep), data= Soybean1)

qqnorm(resid(sb_stand))

plot(sb_stand)
#assumptions satisfactorily met

anova(sb_stand)
#site-year fixed effect significant.
```

```{r}
sb_cc_stand_lsmeans= lsmeans(sb_stand ,~ site_crop_yr, contr="pairwise", adjust="none", type="response")
sb_cc_standCLD<- CLD(sb_cc_stand_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

sb_cc_standCLD <- as_tibble(sb_cc_standCLD) %>% 
  rename(stand_count = lsmean) %>%
  mutate(site_crop_yr = fct_recode(site_crop_yr,
                          "Arlington 2019" = "ARL_SB_19",
                          "Arlington 2020" = "ARL_SB_20",
                          "Havelock 2019" = "HAV_SB_19",
                          "Havelock 2020" = "HAV_SB_20",
                          "Lancaster 2019" = "LAN_SB_19",
                          "Lancaster 2020" = "LAN_SB_20")) %>%
  arrange(site_crop_yr)
```

```{r}
ggplot(sb_cc_standCLD, aes(x= site_crop_yr, y= stand_count, color= site_crop_yr)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3) +
  geom_text(aes(label = .group), nudge_y = 15000, size= 5) +
  geom_jitter(data = Soybean1 ,mapping = aes(y = stand_count), alpha = 0.2) +
  coord_flip() +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Soybean Stand Counts")
```


# Soybean Yield Components

```{r}
Soybean2 %>%
  ggplot(aes(x = Soil, y = Total, color = Soil)) +
  geom_boxplot() +
  facet_grid(~ Site_Yr)

Soybean2 %>%
  ggplot(aes(x = Soil, y = Hundred, color = Soil)) +
  geom_boxplot() +
  facet_grid(~ Site_Yr)

Soybean2 %>%
  ggplot(aes(x = Soil, y = Seeds, color = Soil)) +
  geom_boxplot() +
  facet_grid(~ Site_Yr)

Soybean %>%
  ggplot(aes(x = Soil, y = Pods.Plant, color = Soil)) +
  geom_boxplot() +
  facet_grid(~ Site_Yr)

Soybean %>%
  ggplot(aes(x = Soil, y = Seeds.Pod, color = Soil)) +
  geom_boxplot() +
  facet_grid(~ Site_Yr)
```


## Pods.Plant By Location

### Havelock
```{r}
arl_SBPods_Plant= lmer(Pods.Plant~Soil*Herb+ (1|Rep/Year) , data= (filter(Soybean, Location == "HAV")))
qqnorm(resid(arl_SBPods_Plant))
plot(arl_SBPods_Plant)

arl_SBPods_Plant1= lmer(sqrt(Pods.Plant)~Soil*Herb+ (1|Rep/Year) , data= (filter(Soybean, Location == "HAV")))
qqnorm(resid(arl_SBPods_Plant1))
plot(arl_SBPods_Plant1)

arl_SBPods_Plant2= lmer(log(Pods.Plant)~Soil*Herb+ (1|Rep/Year) , data= (filter(Soybean, Location == "HAV")))
qqnorm(resid(arl_SBPods_Plant2))
plot(arl_SBPods_Plant2)
# go with log transformation
```

```{r}
anova(arl_SBPods_Plant2)
#nothing significant
```





```{r}
Soybean1 %>% 
  ggplot(aes(x =Total)) +
  geom_density()

Soybean1 %>% 
  ggplot(aes(x =Hundred)) +
  geom_density()

Soybean %>% 
  ggplot(aes(x =Seeds)) +
  geom_density()
#skewed

Soybean %>% 
  ggplot(aes(x =Pods.Plant)) +
  geom_density()
#skewed

Soybean %>% 
  ggplot(aes(x =Seeds.Pod)) +
  geom_density()
#skewed
```




## SB 2020 Total Sample Mass
```{r, fig.show='hide'}
SBTotal= lmer(Total~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean1)
qqnorm(resid(SBTotal))
plot(SBTotal)
#Based on visual assessment, assumptions for a normal distribution and equal variance appear to be met. Proceed with ANOVA

```

### ANOVA of untransformed SB total sample mass model
```{r, echo=FALSE}
anova(SBTotal)
#Site-Year fixed effect significant
```

### SB total sample means comparison for Significant Site-Year fixed effect
```{r, echo=FALSE}
SBTotMeans= lsmeans(SBTotal, ~ Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD4= CLD(SBTotMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD4
```

```{r, echo= FALSE, include= FALSE}
SBTot= ggplot(CLD4, aes(x=Site_Yr , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 20, size = 8)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Soybean Total sample Mass", x= "Site-Year", y= "Sample Mass (g)")
```

```{r, echo= FALSE, include= FALSE}
SBTot
```


## SB 2020 100 Seed Weight
```{r, fig.show='hide'}
SBHundred= lmer(Hundred~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean1)
qqnorm(resid(SBHundred))
plot(SBHundred)
#Based on visual assessment, assumptions for a normal distribution and equal variance appear to be met. Proceed with ANOVA

```

### ANOVA of untransformed SB seed density model
```{r, echo=FALSE}
anova(SBHundred)
#Site-year and soil management fixed effects significant
```

### SB seed density means comparisons for Significant soil and Site-Year fixed effects
```{r, echo=FALSE}
SBHundred_SoilMeans= lsmeans(SBHundred, ~ Soil, contr="pairwise", adjust="none", type= "response")
CLD5= CLD(SBHundred_SoilMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD5

SBHundred_SiteMeans= lsmeans(SBHundred, ~ Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD6= CLD(SBHundred_SiteMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD6
```

```{r, echo= FALSE, include= FALSE}
SBDensitySoil=ggplot(CLD5, aes(x= Soil , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 0.5, size = 8)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Soybean Seed density - Soil Management", x= "Soil Managment", y= "100 Seed Weight")

SBDensitySite= ggplot(CLD6, aes(x=Site_Yr , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 0.6, size = 8)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Soybean Seed Density - Site-Year", x= "Site-Year", y= "100 Seed Weight")
```

```{r, echo= FALSE, include= FALSE}
SBDensitySoil

SBDensitySite
```


## Soybean Seed Counts
```{r}
SBSeeds= lmer(Seeds~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean)
qqnorm(resid(SBSeeds))
plot(SBSeeds)
#Look at transforming data. Not satisfied.

SBSeeds1= lmer(log(Seeds)~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean)
qqnorm(resid(SBSeeds1))
plot(SBSeeds1)
#looks way better. Use this one

SBSeeds2= lmer((sqrt(Seeds))~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean)
qqnorm(resid(SBSeeds2))
plot(SBSeeds2)
#looks slightly better
```

### ANOVA of log transformed SB total seeds model
```{r}
anova(SBSeeds1)
#3-way interaction between site-Year, soil management, and herbicide treatment. Site-Year fixed effect significant
```

### SB total seeds means comparison for Significant Soil:Herbicide:Site-Year interaction
```{r, include= FALSE, echo= FALSE}
SBSeeds_Means= lsmeans(SBSeeds1, ~ Soil*Herb|Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD7= CLD(SBSeeds_Means, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD7
```
Didn't include to keep PDF size smaller. It was a 3-way interactions so big and messy. See figure at end!

```{r, echo= FALSE, include= FALSE}
SBSeeds= ggplot(CLD7, aes(x= Herb, y= response, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 250, size = 4)+
  facet_grid(Soil~Site_Yr)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Soybean Seed Count", x= "Herbicide Treatment", y= "# of Seeds")
```

```{r, echo= FALSE, include= FALSE}
SBSeeds
```

## Soybean Pods/Plant
```{r}
SBPods_Plant= lmer(Pods.Plant~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean)
qqnorm(resid(SBPods_Plant))
plot(SBPods_Plant)
#tranform!

SBPods_Plant1= lmer(sqrt(Pods.Plant)~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean)
qqnorm(resid(SBPods_Plant1))
plot(SBPods_Plant1)

SBPods_Plant2= lmer(log(Pods.Plant)~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean)
qqnorm(resid(SBPods_Plant2))
plot(SBPods_Plant2)
#went with this transformation
```

### ANOVA of log transformed SB pods/plant model
```{r}
anova(SBPods_Plant2)
#Site-year fixed effect significant
```

### SB pods/plant means comparison for Significant Site-Year fixed effect
```{r, echo= FALSE}
SBPods_PlantMeans= lsmeans(SBPods_Plant2, ~ Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD8= CLD(SBPods_PlantMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD8
```

```{r, include= FALSE, echo= FALSE}
SBPods_Plant= ggplot(CLD8, aes(x=Site_Yr , y=response, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 0.6, size = 8)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Soybean Pods/Plant - Site-Year", x= "Site-Year", y= "# Pods/Plant")
```

```{r, include= FALSE,echo= FALSE}
SBPods_Plant
```

## Soybean Seeds/Pod
```{r, fig.show='hide'}
SBSeeds_Pod= lmer(Seeds.Pod~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean)
qqnorm(resid(SBSeeds_Pod))
plot(SBSeeds_Pod)
#Assumption for normal distribution and equal variance met satisfactorily.
```

### ANOVA of untransformed SB seeds/pod model
```{r, echo=FALSE}
anova(SBSeeds_Pod)
#Site-Year:Soil management and Site-year:Herbicide 2-way interactions significant. Site-Year main effect also significant
```

### SB seeds/pod means comparison for Significant Soil:Site-Year and Herb:Site-Year interactions
```{r, echo=FALSE}
SBSeeds_PodSoilMeans= lsmeans(SBSeeds_Pod, ~ Soil|Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD9= CLD(SBSeeds_PodSoilMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD9

SBSeeds_PodHerbMeans= lsmeans(SBSeeds_Pod, ~ Herb|Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD10= CLD(SBSeeds_PodHerbMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD10
```

```{r, include= FALSE, echo= FALSE}
SBSeeds_Pod_Soil= ggplot(CLD9, aes(x= Soil, y=lsmean, label= .group))+
  facet_grid(~Site_Yr)+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 0.6, size = 8)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Soybean Seeds/Pod - Soil Management", x= "Soil Management Practice", y= "# Seeds/Pod")
   
SBSeeds_Pod_Herb= ggplot(CLD10, aes(x= Herb, y=lsmean, label= .group))+
  facet_grid(~Site_Yr)+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 0.6, size = 8)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Soybean Seeds/Pod - Herbicide Treatment", x= "Herbicide Treatment", y= "# Seeds/Pod")
```

```{r, include= FALSE, echo= FALSE}
SBSeeds_Pod_Soil

SBSeeds_Pod_Herb
```

## Soybean Yield Component Figures
```{r}
SBTot
SBDensitySoil
SBDensitySite
SBSeeds
SBPods_Plant
SBSeeds_Pod_Soil
SBSeeds_Pod_Herb
```

# Soybean Yield

```{r}
Soybean1 %>%
  ggplot(aes(x = soil, y = yield, color = location)) +
  geom_boxplot() +
  facet_grid(crop ~ year)
```

### Arlington Analysis
```{r}
arl_sb_yield= lmer(yield~ soil*herb + (1|rep/year), data= (filter(Soybean1, location == "Arlington")))
summary(arl_sb_yield)

qqnorm(resid(arl_sb_yield))

plot(arl_sb_yield)
#assumptions look good

anova(arl_sb_yield)
#Soil management fixed effect significant
```

### Lancaster Analysis
```{r}
lan_sb_yield= lmer(yield~ soil*herb + (1|rep/year), data= (filter(Soybean1, location == "Lancaster")))

qqnorm(resid(lan_sb_yield))

plot(lan_sb_yield)
#assumptions look good

anova(lan_sb_yield)
#Soil management fixed effect significant
```

### Havelock Analysis
```{r}
hav_sb_yield= lmer(yield~ soil*herb + (1|rep/year), data= (filter(Soybean1, location == "Havelock")))

qqnorm(resid(hav_sb_yield))

plot(hav_sb_yield)
#assumptions look good

anova(hav_sb_yield)
#nothing significant
```

```{r, echo= FALSE, include= FALSE}
arl_sb_lsmeans<- lsmeans(arl_sb_yield, ~ soil, contr="pairwise", adjust="none")

arl_sb_cld <- cld(arl_sb_lsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

arl_sb_cld <- as_tibble(arl_sb_cld) %>% 
  rename(yield = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, echo= FALSE, include= FALSE}
lan_sb_lsmeans<- lsmeans(lan_sb_yield, ~ soil, contr="pairwise", adjust="none")

lan_sb_cld <- cld(lan_sb_lsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan_sb_cld <- as_tibble(lan_sb_cld) %>% 
  rename(yield = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, echo= FALSE, include= FALSE}
hav_sb_lsmeans<- lsmeans(hav_sb_yield, ~ soil, contr="pairwise", adjust="none")

hav_sb_cld <- cld(hav_sb_lsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav_sb_cld <- as_tibble(hav_sb_cld) %>% 
  rename(yield = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, echo= FALSE, include= FALSE}
arl_sb_cld$location= c("Arlington")
lan_sb_cld$location= c('Lancaster')
hav_sb_cld$location= c('Havelock')

sbyield<- rbind(arl_sb_cld, sbyield)
sbyield<- rbind(lan_sb_cld, sbyield)
sbyield<- rbind(hav_sb_cld, sbyield)
```

```{r}
y2<- ggplot(sbyield, aes(x= soil, y= yield, color= soil)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3) +
  geom_text(aes(label = .group), nudge_y = 800) +
  geom_jitter(data = Soybean1 ,mapping = aes(y = yield), alpha = 0.2) +
  #coord_flip() +
  facet_grid(~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Soybean Yield")

y2
```



# Crop Canopy

```{r}
Soybean1 %>%
  ggplot(aes(x = soil, y = crop_canopy, color = location)) +
  geom_boxplot() +
  facet_grid(~ year)
```

Based on the variability in canopy coverage between cropping seasons for both crops, I will create a simplified model with for all of them and then separating means with this model as well as models for each site-crop year.


## Soybean Canopy

# Simplified model
```{r}
sb_canopy = glmmTMB(crop_canopy~ soil*herb*site_crop_yr + (1|rep:site_crop_yr), data= Soybean1, beta_family(link="logit"))

Anova(sb_canopy)
#all 3 main fixed effects significant and the soil:site-year interaction
```

```{r}
sb_canopy_herbemmeans = emmeans(sb_canopy, ~ herb, contr= "pairwise", adjust= "none", type= "response")
sb_canopy_herbCLD = CLD(sb_canopy_herbemmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

sb_canopy_soilemmeans = emmeans(sb_canopy, ~ soil|site_crop_yr, contr= "pairwise", adjust= "none", type= "response")
sb_canopy_soilCLD = CLD(sb_canopy_soilemmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

sb_canopy_herbCLD <- as_tibble(sb_canopy_herbCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(herb= factor(herb, levels= order2)) %>%
  arrange(herb)

sb_canopy_soilCLD <- as_tibble(sb_canopy_soilCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```



### Arlington Soy Canopy
```{r}
arl19_soy_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Soybean1, site_crop_yr == "Arlington 2019")), beta_family(link="logit"))

Anova(arl19_soy_can)
#Soil and herb fixed effects significant

arl20_soy_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Soybean1, site_crop_yr == "Arlington 2020")), beta_family(link="logit"))

Anova(arl20_soy_can)
#nothing significant
```

```{r, echo= FALSE, include= FALSE}
arl19_soy_can_lsmeans= emmeans(arl19_soy_can ,~ soil, contr="pairwise", adjust="none", type="response")
arl19_soy_canCLD<- CLD(arl19_soy_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

arl19_soy_canCLD <- as_tibble(arl19_soy_canCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)

arl19_soy_can_herblsmeans= emmeans(arl19_soy_can ,~ herb, contr="pairwise", adjust="none", type="response")
arl19_soy_canherbCLD<- CLD(arl19_soy_can_herblsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

arl19_soy_canherbCLD <- as_tibble(arl19_soy_canherbCLD) %>%
  rename(crop_canopy = response)%>%
  mutate(herb= factor(herb, levels= order2)) %>%
  arrange(herb)

arl20_soy_can_lsmeans= emmeans(arl20_soy_can ,~ soil, contr="pairwise", adjust="none", type="response")
arl20_soy_canCLD<- CLD(arl20_soy_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

arl20_soy_canCLD <- as_tibble(arl20_soy_canCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)

arl20_soy_can_herblsmeans= emmeans(arl20_soy_can ,~ herb, contr="pairwise", adjust="none", type="response")
arl20_soy_canherbCLD<- CLD(arl20_soy_can_herblsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

arl20_soy_canherbCLD <- as_tibble(arl20_soy_canherbCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(herb= factor(herb, levels= order2)) %>%
  arrange(herb)
```


### Lancaster Soy Canopy
```{r}
lan19_soy_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Soybean1, site_crop_yr == "Lancaster 2019")), beta_family(link="logit"))

Anova(lan19_soy_can)
#Soil was significant

lan20_soy_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Soybean1, site_crop_yr == "Lancaster 2020")), beta_family(link="logit"))

Anova(lan20_soy_can)
#nothing significant
```


```{r, echo= FALSE, include= FALSE}
lan19_soy_can_lsmeans= emmeans(lan19_soy_can ,~ soil, contr="pairwise", adjust="none", type="response")
lan19_soy_canCLD<- CLD(lan19_soy_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan19_soy_canCLD <- as_tibble(lan19_soy_canCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)

lan19_soy_can_herblsmeans= emmeans(lan19_soy_can ,~ herb, contr="pairwise", adjust="none", type="response")
lan19_soy_canherbCLD<- CLD(lan19_soy_can_herblsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan19_soy_canherbCLD <- as_tibble(lan19_soy_canherbCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(herb= factor(herb, levels= order2)) %>%
  arrange(herb)

lan20_soy_can_lsmeans= emmeans(lan20_soy_can ,~ soil, contr="pairwise", adjust="none", type="response")
lan20_soy_canCLD<- CLD(lan20_soy_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan20_soy_canCLD <- as_tibble(lan20_soy_canCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)

lan20_soy_can_herblsmeans= emmeans(lan20_soy_can ,~ herb, contr="pairwise", adjust="none", type="response")
lan20_soy_canherbCLD<- CLD(lan20_soy_can_herblsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan20_soy_canherbCLD <- as_tibble(lan20_soy_canherbCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(herb= factor(herb, levels= order2)) %>%
  arrange(herb)
```


### Havelock Soy Canopy
```{r}
hav19_soy_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Soybean1, site_crop_yr == "Havelock 2019")), beta_family(link="logit"))

Anova(hav19_soy_can)
#Soil and herbicide fixed effects were significant

hav20_soy_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Soybean1, site_crop_yr == "Havelock 2020")), beta_family(link="logit"))

Anova(hav20_soy_can)
#Soil and herbicide fixed effects were significant
```

```{r, echo= FALSE, include= FALSE}
hav19_soy_can_lsmeans= emmeans(hav19_soy_can ,~ soil, contr="pairwise", adjust="none", type="response")
hav19_soy_canCLD<- CLD(hav19_soy_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav19_soy_canCLD <- as_tibble(hav19_soy_canCLD) %>%
 rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)

hav19_soy_can_herblsmeans= emmeans(hav19_soy_can ,~ herb, contr="pairwise", adjust="none", type="response")
hav19_soy_canherbCLD<- CLD(hav19_soy_can_herblsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav19_soy_canherbCLD <- as_tibble(hav19_soy_canherbCLD) %>%
 rename(crop_canopy = response) %>%
  mutate(herb= factor(herb, levels= order2)) %>%
  arrange(herb)

hav20_soy_can_lsmeans= emmeans(hav20_soy_can ,~ soil, contr="pairwise", adjust="none", type="response")
hav20_soy_canCLD<- CLD(hav20_soy_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav20_soy_canCLD <- as_tibble(hav20_soy_canCLD) %>%
 rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)

hav20_soy_can_herblsmeans= emmeans(hav20_soy_can ,~ herb, contr="pairwise", adjust="none", type="response")
hav20_soy_canherbCLD<- CLD(hav20_soy_can_herblsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav20_soy_canherbCLD <- as_tibble(hav20_soy_canherbCLD) %>%
 rename(crop_canopy = response) %>%
  mutate(herb= factor(herb, levels= order2)) %>%
  arrange(herb)
```

```{r, echo= FALSE, include= FALSE}
sbcanopy= data.frame()

arl19_soy_canCLD$location= c("Arlington")
arl20_soy_canCLD$location= c("Arlington")
lan19_soy_canCLD$location= c("Lancaster")
lan20_soy_canCLD$location= c("Lancaster")
hav19_soy_canCLD$location= c("Havelock")
hav20_soy_canCLD$location= c("Havelock")

arl19_soy_canCLD$year= c("2019")
arl20_soy_canCLD$year= c("2020")
lan19_soy_canCLD$year= c("2019")
lan20_soy_canCLD$year= c("2020")
hav19_soy_canCLD$year= c("2019")
hav20_soy_canCLD$year= c("2020")

sbcanopy<- rbind(arl19_soy_canCLD, sbcanopy)
sbcanopy<- rbind(arl20_soy_canCLD, sbcanopy)
sbcanopy<- rbind(lan19_soy_canCLD, sbcanopy)
sbcanopy<- rbind(lan20_soy_canCLD, sbcanopy)
sbcanopy<- rbind(hav19_soy_canCLD, sbcanopy)
sbcanopy<- rbind(hav20_soy_canCLD, sbcanopy)
```

```{r, echo= FALSE, include= FALSE}
sbcanopy2= data.frame()

arl19_soy_canherbCLD$location= c("Arlington")
arl20_soy_canherbCLD$location= c("Arlington")
lan19_soy_canherbCLD$location= c("Lancaster")
lan20_soy_canherbCLD$location= c("Lancaster")
hav19_soy_canherbCLD$location= c("Havelock")
hav20_soy_canherbCLD$location= c("Havelock")

arl19_soy_canherbCLD$year= c("2019")
arl20_soy_canherbCLD$year= c("2020")
lan19_soy_canherbCLD$year= c("2019")
lan20_soy_canherbCLD$year= c("2020")
hav19_soy_canherbCLD$year= c("2019")
hav20_soy_canherbCLD$year= c("2020")

sbcanopy2<- rbind(arl19_soy_canherbCLD, sbcanopy2)
sbcanopy2<- rbind(arl20_soy_canherbCLD, sbcanopy2)
sbcanopy2<- rbind(lan19_soy_canherbCLD, sbcanopy2)
sbcanopy2<- rbind(lan20_soy_canherbCLD, sbcanopy2)
sbcanopy2<- rbind(hav19_soy_canherbCLD, sbcanopy2)
sbcanopy2<- rbind(hav20_soy_canherbCLD, sbcanopy2)
```



```{r}
sb_canopy <- ggplot(sb_canopy_soilCLD, aes(x= soil, y= crop_canopy*100, color= soil)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL*100, ymax= upper.CL*100), width= .3) +
  geom_text(aes(label = .group), nudge_y = 12) +
  geom_jitter(data = Soybean1 ,mapping = aes(y = crop_canopy*100), alpha = 0.2) +
  #coord_flip() +
  facet_wrap(~site_crop_yr) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Soybean Canopy")

```



```{r}
sb_canopy1 <- ggplot(sbcanopy, aes(x= soil, y= crop_canopy*100, color= soil)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL*100, ymax= upper.CL*100), width= .3) +
  geom_text(aes(label = .group), nudge_y = 10) +
  geom_jitter(data = Soybean1 ,mapping = aes(y = crop_canopy*100), alpha = 0.2) +
  #coord_flip() +
  facet_grid(year~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Soybean Canopy")
```

Results are very similar for all site-years with the soybean canopy models. 



```{r}
sb_canopyherb <- ggplot(sb_canopy_herbCLD, aes(x= herb, y= crop_canopy*100, color= herb)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL*100, ymax= upper.CL*100), width= .3) +
  geom_text(aes(label = .group), nudge_y = 4) +
  geom_jitter(data = Soybean1 ,mapping = aes(y = crop_canopy*100), alpha = 0.2) +
  #coord_flip() +
  #facet_grid(year~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Soybean Canopy")
```

```{r}
sb_canopyherb1 <- ggplot(sbcanopy2, aes(x= herb, y= crop_canopy*100, color= herb)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL*100, ymax= upper.CL*100), width= .3) +
  geom_text(aes(label = .group), nudge_y = 10) +
  geom_jitter(data = Soybean1 ,mapping = aes(y = crop_canopy*100), alpha = 0.2) +
  #coord_flip() +
  facet_grid(year~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Soybean Canopy")
```


In the analysis with separate models for every site-year it seems weird that the control trt ends up with a lower canopy coverage compared to some of the herbicide trts at Havelock 2019. Personally I prefer the simplified analyses with one model for all site-years to keep things straightforward.



# Cover Crop Biomass analysis
```{r}
SBCC %>%
  ggplot(aes(x = herb, y = biomass_kg, color = site)) +
  geom_boxplot() +
  facet_grid(crop ~ year)
```
based on separations between locations and across years, I think it is appropriate to look for significant differences between site-years and separate means accordingly in CC biomass models.

### Soybean
```{r}
sb_cc_bio= lmer(biomass_kg~ site_crop_yr * herb + (1|site_crop_yr:rep), data=SBCC)

qqnorm(resid(sb_cc_bio))
plot(sb_cc_bio)
#assumptions for equal variance not met

sb_cc_bio1= lmer(sqrt(biomass_kg)~ site_crop_yr * herb + (1|site_crop_yr:rep), data=SBCC)

qqnorm(resid(sb_cc_bio1))
plot(sb_cc_bio1)
#assumption improved. Maybe clean datapoint

anova(sb_cc_bio1)
#Site-year significant
```


```{r}
sb_cc_lsmeans= emmeans(sb_cc_bio1 ,~ site_crop_yr, contr="pairwise", adjust="none", type="response")
sb_ccCLD<- CLD(sb_cc_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

sb_ccCLD <- as_tibble(sb_ccCLD) %>%
 rename(biomass_kg = response)
```

```{r}
Soy_CCbio= ggplot(sb_ccCLD, aes(x= site_crop_yr, y= biomass_kg, color= site_crop_yr)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3) +
  geom_text(aes(label = .group), nudge_y = 150, size= 5) +
  geom_jitter(data = SBCC ,mapping = aes(y = biomass_kg), alpha = 0.2) +
  coord_flip() +
  #facet_grid(year~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Soybean")
```



# Cover Crop Canopy


```{r}
SBCC1 %>%
  ggplot(aes(x = herb, y = canopy, color = site)) +
  geom_boxplot() +
  facet_grid(crop ~ year)
```

Based on differences between location across growing seasons I thought it was best to proceed with testing site-year as a fixed effect.

### Soybean
```{r}
SBCC1 <- SBCC %>%
  filter(!is.na(canopy))
```


```{r}
sb_cc_can= glmmTMB(canopy~ site_crop_yr*herb + (1|site_crop_yr:rep), data=SBCC, beta_family(link="logit"))

Anova(sb_cc_bio)
#Site-Year significant
```

```{r}
sb_cc_can_lsmeans= emmeans(sb_cc_can ,~ site_crop_yr, contr="pairwise", adjust="none", type="response")
sb_cc_canCLD<- CLD(sb_cc_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

sb_cc_canCLD <- as_tibble(sb_cc_canCLD) %>%
 rename(canopy = response)
```


```{r}
Soy_CCcan= ggplot(sb_cc_canCLD, aes(x= site_crop_yr, y= canopy*100, color= site_crop_yr)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL*100, ymax= upper.CL*100), width= .3) +
  geom_text(aes(label = .group), nudge_y = 5, size= 5) +
  geom_jitter(data = SBCC1 ,mapping = aes(y = canopy*100), alpha = 0.2) +
  coord_flip() +
  #facet_grid(year~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Soybean")
```




