---
title: "Carryover_CornResults"
author: "Kolby Grint"
date: "3/4/2021"
output: pdf_document
---


```{r, include= FALSE}

library(car)
library(ggplot2)
library(emmeans)
library(lme4)
library(lmerTest)
library(patchwork)
library(glmmTMB)
library(dplyr)
library(tidyverse)
library(multcomp)
```


```{r, }
getwd()

Corn= read.csv(file="Corn_MasterData.csv")

CC= read.csv(file= "CoverCropData.csv")

cnyield= data.frame()

order= c("Tillage", "No-Till", "Cover Crop")
order1= c("CTRL", "FO25", "FO50", "IM25", "IM50")

CornComp= read.csv(file="CornYieldComponents.csv")
Corn$Rep= factor(Corn$Rep)
Corn$Year= factor(Corn$Year)


```


```{r,}
Corn1 <- Corn %>% 
  mutate(Rep = as_factor(Rep),
         Year = as_factor(Year),
         Soil= fct_recode(Soil, 
                          "Cover Crop" = "CC",
                          "No-Till" = "NT",
                          "Tillage" = "Till"),
         Site_crop_yr = fct_recode(Site_crop_yr,
                          "Arlington 2019" = "ARL_CN_19",
                          "Arlington 2020" = "ARL_CN_20",
                          "Havelock 2019" = "HAV_CN_19",
                          "Havelock 2020" = "HAV_CN_20",
                          "Lancaster 2019" = "LAN_CN_19",
                          "Lancaster 2020" = "LAN_CN_20"),
         Crop.Canopy = round(Crop.Canopy/100, 2),
         yield = round(yield, 5)) %>%
  filter(!is.na(yield)) %>%
  filter(!is.na(Crop.Canopy)) %>%
  filter(!is.na(Stand.Count)) %>%
  janitor::clean_names()

CornCC <- CC %>%
  filter(Crop == "Corn") %>%
  mutate(Rep = as_factor(Rep),
         Year = as_factor(Year),
         Site_Crop_Yr = fct_recode(Site_crop_yr,
                          "Arlington 2019" = "ARL_CN_19",
                          "Arlington 2020"  = "ARL_CN_20",
                          "Havelock 2019" = "HAV_CN_19",
                          "Havelock 2020" = "HAV_CN_20",
                          "Lancaster 2019" = "LAN_CN_19",
                          "Lancaster 2020" = "LAN_CN_20"),
         Canopy = round(Canopy/100, 3)) %>%
  filter(!is.na(Biomass_kg)) %>%
  filter(!is.na(Site_crop_yr)) %>% 
  filter(!Site_crop_yr == "ARL_CN_20") %>%
  janitor::clean_names()


CornComp= CornComp %>% 
  mutate(Location = fct_recode(Location,
                               "Arlington" = "ARL",
                               "Lancaster" = "LAN",
                               "Havelock" = "HAV"),
         Soil = fct_recode(Soil,
                           "Cover Crop" = "CC",
                          "No-Till" = "NT",
                          "Tillage" = "Till")) %>%
  filter(Site_Yr != "ARL_20") %>%
  filter(!is.na(Total)) %>%
  filter(!is.na(Hundred)) %>%
  filter(!is.na(Seeds))

```


# Stand Counts

```{r, fig.width= 12, fig.height= 6}
Corn1 %>%
  ggplot(aes(x = soil, y = stand_count, color = location)) +
  geom_boxplot() +
  facet_grid(crop ~ year)
```

```{r, fig.width= 12, fig.height= 6}
Corn1 %>%
  ggplot(aes(x = herb, y = stand_count, color = location)) +
  geom_boxplot() +
  facet_grid(soil ~ year)

```

Based on these visual representations it doesn't appear to me that there are really any consistent patterns as a function of soil management, herbicide treatment, location, or year. There does appear to be differences in location across seasons. Therefore, I think it is best if we test for site-year differences as a fixed effect in models for our initial approach and separate means by site-year where appropriate.

```{r, echo= FALSE, include= FALSE}
Corn1 <- Corn1 %>%
  filter(!site_crop_yr == "Arlington 2020")
```

```{r}
cn_stand= lmer(stand_count ~ site_crop_yr*soil*herb + (1|site_crop_yr:rep), data= Corn1)

qqnorm(resid(cn_stand))

plot(cn_stand)
#assumptions met satisfactorily

anova(cn_stand)
#site-year significant
```


```{r}
cn_cc_stand_lsmeans= lsmeans(cn_stand ,~ site_crop_yr, contr="pairwise", adjust="none", type="response")
cn_cc_standCLD<- CLD(cn_cc_stand_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

cn_cc_standCLD <- as_tibble(cn_cc_standCLD) %>% 
  rename(stand_count = lsmean) %>%
  mutate(site_crop_yr = fct_recode(site_crop_yr,
                          "Arlington 2019" = "ARL_CN_19",
                          "Havelock 2019" = "HAV_CN_19",
                          "Havelock 2020" = "HAV_CN_20",
                          "Lancaster 2019" = "LAN_CN_19",
                          "Lancaster 2020" = "LAN_CN_20")) %>%
  arrange(site_crop_yr)
```

```{r}
ggplot(cn_cc_standCLD, aes(x= site_crop_yr, y= stand_count, color= site_crop_yr)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3) +
  geom_text(aes(label = .group), nudge_y = 3500, size= 5) +
  geom_jitter(data = Corn1 ,mapping = aes(y = stand_count), alpha = 0.2) +
  coord_flip() +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Corn Stand Counts")
```

# Corn Yield Components

```{r}
CornComp %>% 
  ggplot(aes(x =Total)) +
  geom_density()

CornComp %>% 
  ggplot(aes(x =Hundred)) +
  geom_density()

CornComp %>% 
  ggplot(aes(x =Seeds)) +
  geom_density()
```


```{r}
CornComp %>%
  ggplot(aes(x = Soil, y = Total, color = Soil)) +
  geom_boxplot() +
  facet_grid(~ Site_Yr)

CornComp %>%
  ggplot(aes(x = Soil, y = Hundred, color = Soil)) +
  geom_boxplot() +
  facet_grid(~ Site_Yr)

CornComp %>%
  ggplot(aes(x = Soil, y = Seeds, color = Soil)) +
  geom_boxplot() +
  facet_grid(~ Site_Yr)
```

Based on these figures I think it would be appropriate to conduct analyses for each location separately.


# Corn Total Sample Mass


## Analysis by Location

### Arlington

```{r}
arl_CNTotal= lmer(Total~ Soil*Herb + (1|Rep) , data= (filter(CornComp, Location == "Arlington" )))
qqnorm(resid(arl_CNTotal))
plot(arl_CNTotal)
#Assumptions met

anova(arl_CNTotal)
#Nothing significant
```
### Lancaster
```{r}
lan_CNTotal= lmer(Total~ Soil*Herb + (1|Rep/Year) , data= (filter(CornComp, Location == "Lancaster" )))
qqnorm(resid(lan_CNTotal))
plot(lan_CNTotal)
#Assumptions met

anova(lan_CNTotal)
#Soil significant
```

### Havelock
```{r}
hav_CNTotal= lmer(Total~ Soil*Herb + (1|Rep/Year) , data= (filter(CornComp, Location == "Havelock" )))
qqnorm(resid(hav_CNTotal))
plot(hav_CNTotal)
#Assumptions met

anova(hav_CNTotal)
#Nothing significant
```

```{r}
arl_cn_Totallsmeans<- lsmeans(arl_CNTotal, ~ Soil, contr="pairwise", adjust="none")

arl_cn_Totalcld <- cld(arl_cn_Totallsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

arl_cn_Totalcld <- as_tibble(arl_cn_Totalcld) %>% 
  rename(Total = lsmean) %>%
  mutate(soil= factor(Soil, levels= order)) %>%
  arrange(soil)
```

```{r}
lan_cn_Totallsmeans<- lsmeans(lan_CNTotal, ~ Soil, contr="pairwise", adjust="none")

lan_cn_Totalcld <- cld(lan_cn_Totallsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan_cn_Totalcld <- as_tibble(lan_cn_Totalcld) %>% 
  rename(Total = lsmean) %>%
  mutate(soil= factor(Soil, levels= order)) %>%
  arrange(soil)
```

```{r}
hav_cn_Totallsmeans<- lsmeans(hav_CNTotal, ~ Soil, contr="pairwise", adjust="none")

hav_cn_Totalcld <- cld(hav_cn_Totallsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav_cn_Totalcld <- as_tibble(hav_cn_Totalcld) %>% 
  rename(Total = lsmean) %>%
  mutate(soil= factor(Soil, levels= order)) %>%
  arrange(soil)
```


```{r}
cn_Total= data.frame()

arl_cn_Totalcld$Location= c("Arlington")
lan_cn_Totalcld$Location= c("Lancaster")
hav_cn_Totalcld$Location= c("Havelock")

cn_Total<- rbind(arl_cn_Totalcld, cn_Total)
cn_Total<- rbind(lan_cn_Totalcld, cn_Total)
cn_Total<- rbind(hav_cn_Totalcld, cn_Total)

```


```{r}
CNTotal_site<- ggplot(cn_Total, aes(x= Soil, y= Total, color= Soil)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3) +
  geom_text(aes(label = .group), nudge_y = 210) +
  geom_jitter(data = CornComp ,mapping = aes(y = Total), alpha = 0.2) +
  #coord_flip() +
  facet_grid(~Location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Corn Total Sample")
```



## Condensed analysis
```{r, fig.show='hide'}
CNTotal= lmer(Total~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=CornComp)
qqnorm(resid(CNTotal))
plot(CNTotal)
#normality is questionable, data looks a little skewed. Try transforming.

CNTotal1= lmer((Total^2)~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=CornComp)
qqnorm(resid(CNTotal1))
plot(CNTotal1)
#slightly improved on normality maybe. I think I will leave it untransformed since transformation isn't fitting of data type.
```

### ANOVA of untransformed corn total sample mass model
```{r, echo= FALSE}
anova(CNTotal)
#2-way interaction between SIte-year and soil. Site-year and soil management main effects also significant.
```

### Corn total sample means comparison for Soil:Site-Year interaction
```{r, echo=FALSE}
CNTotMeans= lsmeans(CNTotal, ~ Soil|Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD1= CLD(CNTotMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD1
```


```{r, echo= FALSE, include= FALSE}
CNTotal= ggplot(CLD1, aes(x=Soil , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 150, size = 8)+
  facet_grid(~Site_Yr)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Corn Total Sample Mass", x= "Soil Management", y= "Total Sample Mass")

```

```{r, echo= FALSE, include= FALSE}
CNTotal
```

## Corn Seed Density
```{r, fig.show='hide'}
CNHundred= lmer(Hundred~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Corn1)
qqnorm(resid(CNHundred))
plot(CNHundred)
#Assumptions for normality and equal variance satisfactorily met. Proceed with ANOVA.
```

### ANOVA of untransformed Corn Seed Density Model
```{r, echo=FALSE}
anova(CNHundred)
#2-way interaction between SIte-year and soil. Site-year and soil management main effects also significant.
```

### Corn total sample means comparison for Soil:Site-Year interaction
```{r, echo=FALSE}
CNHundredMeans= lsmeans(CNHundred, ~ Soil|Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD2= CLD(CNHundredMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD2
```


```{r, echo= FALSE, include= FALSE}
CNSeedDensity= ggplot(CLD2, aes(x=Soil , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 2, size = 8)+
  facet_grid(~Site_Yr)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Corn Seed Density", x= "Soil Management", y= "100 Seed Weight")

```

```{r, echo= FALSE, include= FALSE}
CNSeedDensity
```

## Corn Seed Count
```{r, fig.show='hide'}
CNSeeds= lmer(Seeds~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Corn1)
qqnorm(resid(CNSeeds))
plot(CNSeeds)
#Normality assumption isn't amazing Proceed to transform

CNSeeds1= lmer((Seeds^2)~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Corn1)
qqnorm(resid(CNSeeds1))
plot(CNSeeds1)
#Assumption for normal distribution improved. This transformation doesn't really make sense for this data, so proceeded with first model.
```

### ANOVA of untransformed Corn Seed Count Model
```{r, echo=FALSE}
anova(CNSeeds)
#2-way interaction between SIte-year and soil. Site-year and soil management main effects also significant.
```

### Corn seed count means comparison for Soil:Site-Year interaction
```{r, echo=FALSE}
CNSeedsMeans= lsmeans(CNSeeds, ~ Soil|Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD3= CLD(CNSeedsMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD3
```


```{r, echo= FALSE, include= FALSE}
CNSeeds= ggplot(CLD3, aes(x=Soil , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 400, size = 8)+
  facet_grid(~Site_Yr)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Corn Seed Count", x= "Soil Management", y= "# of Seeds")
```

```{r, echo= FALSE, include= FALSE}
CNSeeds
```

## Corn Figures
```{r, echo= FALSE}
CNTotal
CNSeedDensity
CNSeeds
```

# Corn Yield

```{r}
Corn1 %>%
  ggplot(aes(x = soil, y = yield, color = location)) +
  geom_boxplot() +
  facet_grid(crop ~ year)
```


### Arlington 2019 Analysis ---- We decided to use only this site-year in the paper
```{r}
arlcn_yield1= lmer(yield~ soil*herb + (1|rep:site_crop_yr), data= (filter(Corn1, site_crop_yr == "Arlington 2019")))

qqnorm(resid(arlcn_yield1))

plot(arlcn_yield1)
#assumptions look good

anova(arlcn_yield1)
#soil managment fixed effect significant
```

### Lancaster Analysis
```{r}
lancn_yield= lmer(yield~ soil*herb + (1|rep/year), data= (filter(Corn1, location == "Lancaster")))

qqnorm(resid(lancn_yield))

plot(lancn_yield)
#assumptions look good

anova(lancn_yield)
#Soil management fixed effect significant
```

### Havelock Analysis
```{r}
havcn_yield= lmer(yield~ soil*herb + (1|rep/year), data= (filter(Corn1, location == "Havelock")))
#from my understanding the "boundary (singular) fit: see ?isSingular" error means that the estimate of error between random effects, in this case rep/year is almost zero, meaning there isn't a lot of random variability?

qqnorm(resid(havcn_yield))

plot(havcn_yield)
#assumptions look good

anova(havcn_yield)
#soil management significant

#summary(havcn_yield)

```

```{r, echo= FALSE, include= FALSE}
arl_cn_lsmeans<- lsmeans(arlcn_yield1, ~ soil, contr="pairwise", adjust="none")

arl_cn_cld <- cld(arl_cn_lsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

arl_cn_cld <- as_tibble(arl_cn_cld) %>% 
  rename(yield = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, echo= FALSE, include= FALSE}
lan_cn_lsmeans<- lsmeans(lancn_yield, ~ soil, contr="pairwise", adjust="none")

lan_cn_cld <- cld(lan_cn_lsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan_cn_cld <- as_tibble(lan_cn_cld) %>% 
  rename(yield = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, echo= FALSE, include= FALSE}
hav_cn_lsmeans<- lsmeans(havcn_yield, ~ soil, contr="pairwise", adjust="none")

hav_cn_cld <- cld(hav_cn_lsmeans$lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav_cn_cld <- as_tibble(hav_cn_cld) %>% 
  rename(yield = lsmean) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```


```{r, echo= FALSE, include= FALSE}
arl_cn_cld$location= c("Arlington")
lan_cn_cld$location= c('Lancaster')
hav_cn_cld$location= c('Havelock')

cnyield<- rbind(arl_cn_cld, cnyield)
cnyield<- rbind(lan_cn_cld, cnyield)
cnyield<- rbind(hav_cn_cld, cnyield)
```

```{r}
y1<- ggplot(cnyield, aes(x= soil, y= yield, color= soil)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3) +
  geom_text(aes(label = .group), nudge_y = 2200) +
  geom_jitter(data = Corn1 ,mapping = aes(y = yield), alpha = 0.2) +
  #coord_flip() +
  facet_grid(~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Corn Yield")

y1
```


## Corn Canopy


```{r}
Corn1 %>%
  ggplot(aes(x = soil, y = crop_canopy, color = location)) +
  geom_boxplot() +
  facet_grid(crop ~ year)
```


### Simplified model
```{r}
cn_canopy = glmmTMB(crop_canopy~ soil*herb*site_crop_yr + (1|rep:site_crop_yr), data= Corn1, beta_family(link="logit"))

Anova(cn_canopy)
#all 3 main fixed effects significant and the soil:site-year interaction
```

```{r}
cn_canopy_herbemmeans = emmeans(cn_canopy, ~ herb, contr= "pairwise", adjust= "none", type= "response")
cn_canopy_herbCLD = CLD(cn_canopy_herbemmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

cn_canopy_soilemmeans = emmeans(cn_canopy, ~ soil|site_crop_yr, contr= "pairwise", adjust= "none", type= "response")
cn_canopy_soilCLD = CLD(cn_canopy_soilemmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

cn_canopy_soilCLD <- as_tibble(cn_canopy_soilCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r}

```


### Arlington Corn Canopy
```{r}
arl19_corn_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Corn1, site_crop_yr == "Arlington 2019")), beta_family(link="logit"))

Anova(arl19_corn_can)
#Soil was significant
```

```{r, echo= FALSE, include= FALSE}
arl19_corn_can_lsmeans= emmeans(arl19_corn_can ,~ soil, contr="pairwise", adjust="none", type="response")
arl19_corn_canCLD<- CLD(arl19_corn_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

arl19_corn_canCLD <- as_tibble(arl19_corn_canCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```


### Lancaster Corn Canopy
```{r}
lan19_corn_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Corn1, site_crop_yr == "Lancaster 2019")), beta_family(link="logit"))

Anova(lan19_corn_can)
#Soil was significant

lan20_corn_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Corn1, site_crop_yr == "Lancaster 2020")), beta_family(link="logit"))

Anova(lan20_corn_can)
#Soil was significant
```


```{r, echo= FALSE, include= FALSE}
lan19_corn_can_lsmeans= emmeans(lan19_corn_can ,~ soil, contr="pairwise", adjust="none", type="response")
lan19_corn_canCLD<- CLD(lan19_corn_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan19_corn_canCLD <- as_tibble(lan19_corn_canCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)

lan20_corn_can_lsmeans= emmeans(lan20_corn_can ,~ soil, contr="pairwise", adjust="none", type="response")
lan20_corn_canCLD<- CLD(lan20_corn_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

lan20_corn_canCLD <- as_tibble(lan20_corn_canCLD) %>%
  rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```


### Havelock Corn Canopy
```{r}
hav19_corn_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Corn1, site_crop_yr == "Havelock 2019")), beta_family(link="logit"))

Anova(hav19_corn_can)
#soil management fixed effect was significant

hav20_corn_can = glmmTMB(crop_canopy~ soil*herb + (1|rep:site_crop_yr), data= (filter(Corn1, site_crop_yr == "Havelock 2020")), beta_family(link="logit"))

Anova(hav20_corn_can)
#nothing was significant
```

```{r, echo= FALSE, include= FALSE}
hav19_corn_can_lsmeans= emmeans(hav19_corn_can ,~ soil, contr="pairwise", adjust="none", type="response")
hav19_corn_canCLD<- CLD(hav19_corn_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav19_corn_canCLD <- as_tibble(hav19_corn_canCLD) %>%
 rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)

hav20_corn_can_lsmeans= emmeans(hav20_corn_can ,~ soil, contr="pairwise", adjust="none", type="response")
hav20_corn_canCLD<- CLD(hav20_corn_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

hav20_corn_canCLD <- as_tibble(hav20_corn_canCLD) %>%
 rename(crop_canopy = response) %>%
  mutate(soil= factor(soil, levels= order)) %>%
  arrange(soil)
```

```{r, echo= FALSE, include= FALSE}
cncanopy= data.frame()

arl19_corn_canCLD$location= c("Arlington")
lan19_corn_canCLD$location= c("Lancaster")
lan20_corn_canCLD$location= c("Lancaster")
hav19_corn_canCLD$location= c("Havelock")
hav20_corn_canCLD$location= c("Havelock")

arl19_corn_canCLD$year= c("2019")
lan19_corn_canCLD$year= c("2019")
lan20_corn_canCLD$year= c("2020")
hav19_corn_canCLD$year= c("2019")
hav20_corn_canCLD$year= c("2020")

cncanopy<- rbind(arl19_corn_canCLD, cncanopy)
cncanopy<- rbind(lan19_corn_canCLD, cncanopy)
cncanopy<- rbind(lan20_corn_canCLD, cncanopy)
cncanopy<- rbind(hav19_corn_canCLD, cncanopy)
cncanopy<- rbind(hav20_corn_canCLD, cncanopy)
```


```{r}
cn_canopy <- ggplot(cn_canopy_soilCLD, aes(x= soil, y= crop_canopy*100, color= soil)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL*100, ymax= upper.CL*100), width= .3) +
  geom_text(aes(label = .group), nudge_y = 12) +
  geom_jitter(data = Corn1 ,mapping = aes(y = crop_canopy*100), alpha = 0.2) +
  #coord_flip() +
  facet_wrap(~site_crop_yr) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Corn Canopy")
```


```{r}
cn_canopy1 <- ggplot(cncanopy, aes(x= soil, y= crop_canopy*100, color= soil)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL*100, ymax= upper.CL*100), width= .3) +
  geom_text(aes(label = .group), nudge_y = 12) +
  geom_jitter(data = Corn1 ,mapping = aes(y = crop_canopy*100), alpha = 0.2) +
  #coord_flip() +
  facet_grid(year~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Corn Canopy")
```

The analysis with a separate model for each analysis increased the separation in the Lancaster 2019 site-year


# Cover Crop Biomass analysis
```{r}
CornCC %>%
  ggplot(aes(x = herb, y = biomass_kg, color = site)) +
  geom_boxplot() +
  facet_grid(crop ~ year)
```

### Corn
```{r}

cn_cc_bio= lmer(biomass_kg~ site_crop_yr * herb + (1|site_crop_yr:rep), data=CornCC)

qqnorm(resid(cn_cc_bio))
plot(cn_cc_bio)
#Assumption for equal variance not met

cn_cc_bio1= lmer(sqrt(biomass_kg)~ site_crop_yr * herb + (1|site_crop_yr:rep), data=CornCC)

qqnorm(resid(cn_cc_bio1))
plot(cn_cc_bio1)
#assumptions improved. Use this one!

anova(cn_cc_bio1)
#Site-year significant
```

```{r}
cn_cc_lsmeans= emmeans(cn_cc_bio1 ,~ site_crop_yr, contr="pairwise", adjust="none", type="response")
cn_ccCLD<- CLD(cn_cc_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

cn_ccCLD <- as_tibble(cn_ccCLD) %>%
 rename(biomass_kg = response)
```


```{r}
Corn_CCbio= ggplot(cn_ccCLD, aes(x= site_crop_yr, y= biomass_kg, color= site_crop_yr)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3) +
  geom_text(aes(label = .group), nudge_y = 150, size= 5) +
  geom_jitter(data = CornCC ,mapping = aes(y = biomass_kg), alpha = 0.2) +
  coord_flip() +
  #facet_grid(year~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Corn")
```

### Corn
```{r}

cn_cc_bio= lmer(biomass_kg~ site_crop_yr * herb + (1|site_crop_yr:rep), data=CornCC)

qqnorm(resid(cn_cc_bio))
plot(cn_cc_bio)
#Assumption for equal variance not met

cn_cc_bio1= lmer(sqrt(biomass_kg)~ site_crop_yr * herb + (1|site_crop_yr:rep), data=CornCC)

qqnorm(resid(cn_cc_bio1))
plot(cn_cc_bio1)
#assumptions improved. Use this one!

anova(cn_cc_bio1)
#Site-year significant
```

```{r}
cn_cc_lsmeans= emmeans(cn_cc_bio1 ,~ site_crop_yr, contr="pairwise", adjust="none", type="response")
cn_ccCLD<- CLD(cn_cc_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

cn_ccCLD <- as_tibble(cn_ccCLD) %>%
 rename(biomass_kg = response)
```


```{r}
Corn_CCbio= ggplot(cn_ccCLD, aes(x= site_crop_yr, y= biomass_kg, color= site_crop_yr)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3) +
  geom_text(aes(label = .group), nudge_y = 150, size= 5) +
  geom_jitter(data = CornCC ,mapping = aes(y = biomass_kg), alpha = 0.2) +
  coord_flip() +
  #facet_grid(year~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Corn")
```




# Cover Crop Canopy
### Corn
```{r}
CornCC1 <- CornCC %>%
  filter(!is.na(canopy))

SBCC1 <- SBCC %>%
  filter(!is.na(canopy))
```

```{r}
CornCC1 %>%
  ggplot(aes(x = herb, y = canopy, color = site)) +
  geom_boxplot() +
  facet_grid(crop ~ year)
```

Based on differences between location across growing seasons I thought it was best to proceed with testing site-year as a fixed effect.

```{r}
cn_cc_can= glmmTMB(canopy~ site_crop_yr*herb + (1|site_crop_yr:rep), data=CornCC1, beta_family(link="logit"))

Anova(cn_cc_can)
#Site-year significant
```

```{r}
cn_cc_can_lsmeans= emmeans(cn_cc_can ,~ site_crop_yr, contr="pairwise", adjust="none", type="response")
cn_cc_canCLD<- CLD(cn_cc_can_lsmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)

cn_cc_canCLD <- as_tibble(cn_cc_canCLD) %>%
 rename(canopy = response)
```

```{r}
Corn_CCcan= ggplot(cn_cc_canCLD, aes(x= site_crop_yr, y= canopy*100, color= site_crop_yr)) +
  geom_point(size= 3) +
  geom_errorbar(aes(ymin= lower.CL*100, ymax= upper.CL*100), width= .3) +
  geom_text(aes(label = .group), nudge_y = 5, size= 5) +
  geom_jitter(data = CornCC1,mapping = aes(y = canopy*100), alpha = 0.2) +
  coord_flip() +
  #facet_grid(year~location) +
  theme_bw() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  labs(title = "Corn")
```
