---
title: "Yield Components"
author: "Kolby Grint"
date: "2/7/2021"
output:
  pdf_document: default
  word_document: default
---

```{r, include= FALSE}
library(car)
library(ggplot2)
library(emmeans)
library(lme4)
library(lmerTest)
library(patchwork)
library(glmmTMB)
library(dplyr)
```


```{r, include= FALSE}
getwd()

Corn= read.csv(file="CornYieldComponents.csv")
Corn$Rep= factor(Corn$Rep)
Corn$Year= factor(Corn$Year)

Soybean= read.csv(file="SBYieldComponents.csv")
Soybean$Rep= factor(Soybean$Rep)
Soybean$Year= factor(Soybean$Year)

str(Soybean)
```

### Filter
```{r}
Corn1= Corn %>% 
  filter(Site_Yr != "ARL_20") %>%
  filter(!is.na(Total)) %>%
  filter(!is.na(Hundred)) %>%
  filter(!is.na(Seeds))

  
Corn_ARL20= Corn %>%
  filter(Site_Yr == "ARL_20") %>%
  filter(!is.na(Total)) %>%
  filter(!is.na(Hundred)) %>%
  filter(!is.na(Seeds))

Soybean1= Soybean %>%
  filter(!is.na(Total)) %>%
  filter(!is.na(Hundred)) %>%
  filter(!is.na(Seeds))
```


# Corn Yield Components

```{r}
Corn1 %>% 
  ggplot(aes(x =Total)) +
  geom_density()

Corn1 %>% 
  ggplot(aes(x =Hundred)) +
  geom_density()

Corn1 %>% 
  ggplot(aes(x =Seeds)) +
  geom_density()
```


```{r}
Corn1 %>%
  ggplot(aes(x = Soil, y = Total, color = Soil)) +
  geom_boxplot() +
  facet_grid(~ Site_Yr)

Corn1 %>%
  ggplot(aes(x = Soil, y = Hundred, color = Soil)) +
  geom_boxplot() +
  facet_grid(~ Site_Yr)

Corn1 %>%
  ggplot(aes(x = Soil, y = Seeds, color = Soil)) +
  geom_boxplot() +
  facet_grid(~ Site_Yr)
```




## Corn Total Sample Mass
```{r, fig.show='hide'}
CNTotal= lmer(Total~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Corn1)
qqnorm(resid(CNTotal))
plot(CNTotal)
#normality is questionable, data looks a little skewed. Try transforming.

CNTotal1= lmer((Total^2)~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Corn1)
qqnorm(resid(CNTotal1))
plot(CNTotal1)
#slightly improved on normality maybe. I think I will leave it untransformed since transformation isn't fitting of data type.
```

### ANOVA of untransformed corn total sample mass model
```{r, echo= FALSE}
anova(CNTotal)
#2-way interaction between SIte-year and soil. Site-year and soil management main effects also significant.
```

### Corn total sample means comparison for Soil:Site-Year interaction
```{r, echo=FALSE}
CNTotMeans= lsmeans(CNTotal, ~ Soil|Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD1= CLD(CNTotMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD1
```


```{r, echo= FALSE, include= FALSE}
CNTotal= ggplot(CLD1, aes(x=Soil , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 150, size = 8)+
  facet_grid(~Site_Yr)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Corn Total Sample Mass", x= "Soil Management", y= "Total Sample Mass")

```

```{r, echo= FALSE, include= FALSE}
CNTotal
```

## Corn Seed Density
```{r, fig.show='hide'}
CNHundred= lmer(Hundred~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Corn1)
qqnorm(resid(CNHundred))
plot(CNHundred)
#Assumptions for normality and equal variance satisfactorily met. Proceed with ANOVA.
```

### ANOVA of untransformed Corn Seed Density Model
```{r, echo=FALSE}
anova(CNHundred)
#2-way interaction between SIte-year and soil. Site-year and soil management main effects also significant.
```

### Corn total sample means comparison for Soil:Site-Year interaction
```{r, echo=FALSE}
CNHundredMeans= lsmeans(CNHundred, ~ Soil|Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD2= CLD(CNHundredMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD2
```


```{r, echo= FALSE, include= FALSE}
CNSeedDensity= ggplot(CLD2, aes(x=Soil , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 2, size = 8)+
  facet_grid(~Site_Yr)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Corn Seed Density", x= "Soil Management", y= "100 Seed Weight")

```

```{r, echo= FALSE, include= FALSE}
CNSeedDensity
```

## Corn Seed Count
```{r, fig.show='hide'}
CNSeeds= lmer(Seeds~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Corn1)
qqnorm(resid(CNSeeds))
plot(CNSeeds)
#Normality assumption isn't amazing Proceed to transform

CNSeeds1= lmer((Seeds^2)~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Corn1)
qqnorm(resid(CNSeeds1))
plot(CNSeeds1)
#Assumption for normal distribution improved. This transformation doesn't really make sense for this data, so proceeded with first model.
```

### ANOVA of untransformed Corn Seed Count Model
```{r, echo=FALSE}
anova(CNSeeds)
#2-way interaction between SIte-year and soil. Site-year and soil management main effects also significant.
```

### Corn seed count means comparison for Soil:Site-Year interaction
```{r, echo=FALSE}
CNSeedsMeans= lsmeans(CNSeeds, ~ Soil|Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD3= CLD(CNSeedsMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD3
```


```{r, echo= FALSE, include= FALSE}
CNSeeds= ggplot(CLD3, aes(x=Soil , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 400, size = 8)+
  facet_grid(~Site_Yr)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Corn Seed Count", x= "Soil Management", y= "# of Seeds")
```

```{r, echo= FALSE, include= FALSE}
CNSeeds
```


## Arlington 2020 Corn Analysis
```{r, fig.show='hide'}
ARL20CNTotal= lmer(Total~Soil*Herb+ (1|Rep) , data=Corn_ARL20)
qqnorm(resid(ARL20CNTotal))
plot(ARL20CNTotal)
#Assumptions satisfactory

ARL20CNHundred= lmer(Hundred~Soil*Herb+ (1|Rep) , data=Corn_ARL20)
qqnorm(resid(ARL20CNHundred))
plot(ARL20CNHundred)
#Assumptions for normality and equal variance met.

ARL20CNSeeds= lmer(Seeds~Soil*Herb+ (1|Rep) , data=Corn_ARL20)
qqnorm(resid(ARL20CNSeeds))
plot(ARL20CNSeeds)
#Assumptions satisfactory

```

### ANOVAs of Arlington 2020 corn models
```{r}
anova(ARL20CNTotal)
#nothing significant

anova(ARL20CNHundred)
#nothing significant

anova(ARL20CNSeeds)
#nothing significant
```

## Corn Figures
```{r, echo= FALSE}
CNTotal
CNSeedDensity
CNSeeds
```




# Soybean Yield Components

```{r, include= FALSE, echo= FALSE}
str(Soybean)
```


```{r}
Soybean1 %>% 
  ggplot(aes(x =Total)) +
  geom_density()

Soybean1 %>% 
  ggplot(aes(x =Hundred)) +
  geom_density()

Soybean %>% 
  ggplot(aes(x =Seeds)) +
  geom_density()
#skewed

Soybean %>% 
  ggplot(aes(x =Pods.Plant)) +
  geom_density()
#skewed

Soybean %>% 
  ggplot(aes(x =Seeds.Pod)) +
  geom_density()
#skewed
```


## SB 2020 Total Sample Mass
```{r, fig.show='hide'}
SBTotal= lmer(Total~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean1)
qqnorm(resid(SBTotal))
plot(SBTotal)
#Based on visual assessment, assumptions for a normal distribution and equal variance appear to be met. Proceed with ANOVA

```

### ANOVA of untransformed SB total sample mass model
```{r, echo=FALSE}
anova(SBTotal)
#Site-Year fixed effect significant
```

### SB total sample means comparison for Significant Site-Year fixed effect
```{r, echo=FALSE}
SBTotMeans= lsmeans(SBTotal, ~ Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD4= CLD(SBTotMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD4
```

```{r, echo= FALSE, include= FALSE}
SBTot= ggplot(CLD4, aes(x=Site_Yr , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 20, size = 8)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Soybean Total sample Mass", x= "Site-Year", y= "Sample Mass (g)")
```

```{r, echo= FALSE, include= FALSE}
SBTot
```


## SB 2020 100 Seed Weight
```{r, fig.show='hide'}
SBHundred= lmer(Hundred~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean1)
qqnorm(resid(SBHundred))
plot(SBHundred)
#Based on visual assessment, assumptions for a normal distribution and equal variance appear to be met. Proceed with ANOVA

```

### ANOVA of untransformed SB seed density model
```{r, echo=FALSE}
anova(SBHundred)
#Site-year and soil management fixed effects significant
```

### SB seed density means comparisons for Significant soil and Site-Year fixed effects
```{r, echo=FALSE}
SBHundred_SoilMeans= lsmeans(SBHundred, ~ Soil, contr="pairwise", adjust="none", type= "response")
CLD5= CLD(SBHundred_SoilMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD5

SBHundred_SiteMeans= lsmeans(SBHundred, ~ Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD6= CLD(SBHundred_SiteMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD6
```

```{r, echo= FALSE, include= FALSE}
SBDensitySoil=ggplot(CLD5, aes(x= Soil , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 0.5, size = 8)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Soybean Seed density - Soil Management", x= "Soil Managment", y= "100 Seed Weight")

SBDensitySite= ggplot(CLD6, aes(x=Site_Yr , y=lsmean, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 0.6, size = 8)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Soybean Seed Density - Site-Year", x= "Site-Year", y= "100 Seed Weight")
```

```{r, echo= FALSE, include= FALSE}
SBDensitySoil

SBDensitySite
```


## Soybean Seed Counts
```{r}
SBSeeds= lmer(Seeds~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean)
qqnorm(resid(SBSeeds))
plot(SBSeeds)
#Look at transforming data. Not satisfied.

SBSeeds1= lmer(log(Seeds)~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean)
qqnorm(resid(SBSeeds1))
plot(SBSeeds1)
#looks way better. Use this one

SBSeeds2= lmer((sqrt(Seeds))~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean)
qqnorm(resid(SBSeeds2))
plot(SBSeeds2)
#looks slightly better
```

### ANOVA of log transformed SB total seeds model
```{r}
anova(SBSeeds1)
#3-way interaction between site-Year, soil management, and herbicide treatment. Site-Year fixed effect significant
```

### SB total seeds means comparison for Significant Soil:Herbicide:Site-Year interaction
```{r, include= FALSE, echo= FALSE}
SBSeeds_Means= lsmeans(SBSeeds1, ~ Soil*Herb|Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD7= CLD(SBSeeds_Means, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD7
```
Didn't include to keep PDF size smaller. It was a 3-way interactions so big and messy. See figure at end!

```{r, echo= FALSE, include= FALSE}
SBSeeds= ggplot(CLD7, aes(x= Herb, y= response, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 250, size = 4)+
  facet_grid(Soil~Site_Yr)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Soybean Seed Count", x= "Herbicide Treatment", y= "# of Seeds")
```

```{r, echo= FALSE, include= FALSE}
SBSeeds
```

## Soybean Pods/Plant
```{r}
SBPods_Plant= lmer(Pods.Plant~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean)
qqnorm(resid(SBPods_Plant))
plot(SBPods_Plant)
#tranform!

SBPods_Plant1= lmer(sqrt(Pods.Plant)~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean)
qqnorm(resid(SBPods_Plant1))
plot(SBPods_Plant1)

SBPods_Plant2= lmer(log(Pods.Plant)~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean)
qqnorm(resid(SBPods_Plant2))
plot(SBPods_Plant2)
#went with this transformation
```

### ANOVA of log transformed SB pods/plant model
```{r}
anova(SBPods_Plant2)
#Site-year fixed effect significant
```

### SB pods/plant means comparison for Significant Site-Year fixed effect
```{r, echo= FALSE}
SBPods_PlantMeans= lsmeans(SBPods_Plant2, ~ Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD8= CLD(SBPods_PlantMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD8
```

```{r, include= FALSE, echo= FALSE}
SBPods_Plant= ggplot(CLD8, aes(x=Site_Yr , y=response, label= .group))+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 0.6, size = 8)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Soybean Pods/Plant - Site-Year", x= "Site-Year", y= "# Pods/Plant")
```

```{r, include= FALSE,echo= FALSE}
SBPods_Plant
```

## Soybean Seeds/Pod
```{r, fig.show='hide'}
SBSeeds_Pod= lmer(Seeds.Pod~Site_Yr*Soil*Herb+ (1|Site_Yr:Rep) , data=Soybean)
qqnorm(resid(SBSeeds_Pod))
plot(SBSeeds_Pod)
#Assumption for normal distribution and equal variance met satisfactorily.
```

### ANOVA of untransformed SB seeds/pod model
```{r, echo=FALSE}
anova(SBSeeds_Pod)
#Site-Year:Soil management and Site-year:Herbicide 2-way interactions significant. Site-Year main effect also significant
```

### SB seeds/pod means comparison for Significant Soil:Site-Year and Herb:Site-Year interactions
```{r, echo=FALSE}
SBSeeds_PodSoilMeans= lsmeans(SBSeeds_Pod, ~ Soil|Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD9= CLD(SBSeeds_PodSoilMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD9

SBSeeds_PodHerbMeans= lsmeans(SBSeeds_Pod, ~ Herb|Site_Yr, contr="pairwise", adjust="none", type= "response")
CLD10= CLD(SBSeeds_PodHerbMeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reversed=TRUE)
CLD10
```

```{r, include= FALSE, echo= FALSE}
SBSeeds_Pod_Soil= ggplot(CLD9, aes(x= Soil, y=lsmean, label= .group))+
  facet_grid(~Site_Yr)+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 0.6, size = 8)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Soybean Seeds/Pod - Soil Management", x= "Soil Management Practice", y= "# Seeds/Pod")
   
SBSeeds_Pod_Herb= ggplot(CLD10, aes(x= Herb, y=lsmean, label= .group))+
  facet_grid(~Site_Yr)+
   geom_point(aes(),stat= "identity")+
   geom_text(nudge_y= 0.6, size = 8)+
   geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
  labs(title= "Soybean Seeds/Pod - Herbicide Treatment", x= "Herbicide Treatment", y= "# Seeds/Pod")
```

```{r, include= FALSE, echo= FALSE}
SBSeeds_Pod_Soil

SBSeeds_Pod_Herb
```

## Soybean Yield Component Figures
```{r}
SBTot
SBDensitySoil
SBDensitySite
SBSeeds
SBPods_Plant
SBSeeds_Pod_Soil
SBSeeds_Pod_Herb
```

